---
title: "Team Elo Rating and Trends"
resource_files:
- team_day_ratings_lag.csv
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}

library(plotly); library(dplyr); library(ggplot2); library(shiny)

txt <- element_text(size = 18, colour = "grey25", face = "plain")
bold_txt <- element_text(size = 20, colour = "navy", face = "bold")

theme_standard <- function(base_size = 16, base_family = "") {
  theme_bw(base_size = base_size, base_family = base_family) +
    theme(
      strip.background = element_blank(), 
      
      panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(),
      panel.grid.major.y = element_line( colour = "white", size = 2), 
      panel.grid.major.x = element_line( colour = "white", size = 2), 
      
      #strip.text.x = element_text(size = 24),
      #strip.text.y = element_text(size = 24),
      
      panel.background = element_rect(fill="grey90"),
      plot.background = element_rect(fill="grey90"),
      legend.background = element_rect(fill="grey90"),
      legend.key = element_rect(fill="grey90", size = 20),
      legend.key.size = unit(1,"cm"),
      
      panel.border = element_blank(), 
      
      line = element_line( colour = "white", size = 2),
      axis.text.x = element_text(angle = 90, hjust = 1),
      text = txt, 
      plot.title = bold_txt, 
      
      axis.title = txt, 
      axis.text = txt, 
      
      legend.title = bold_txt, 
      legend.text = txt ) 
}


team_day_ratings <- read.csv("team_day_ratings_lag.csv") %>% 
        mutate(date = as.Date(date, format = "%m/%d/%Y")) %>%
        filter(date != "1997-09-30") %>%
        arrange(date) %>%
        group_by(team) %>%
        mutate(#class = ifelse(max(EloRating) == EloRating, "max",
              #       ifelse(min(EloRating) == EloRating, "min", NA)),
             GameNumber = row_number(),
             Season = as.factor(ifelse(lubridate::month(date) %in% c(9,10,11,12), 
                             paste0(lubridate::year(date), lubridate::year(date) + 1),
                            paste0(lubridate::year(date) - 1, lubridate::year(date))))
             ) %>%
        ungroup()

game_ratings <- reactive({
        
      team_abb <- input$team

      team_day_ratings_team <- team_day_ratings %>%
              filter(team == team_abb)


      return(team_day_ratings_team)

})

game_ratings_scored <- reactive({

      poly_degree <- input$poly_degree

      model <- summary(lm(data = game_ratings(), EloRating ~ poly(GameNumber, degree = poly_degree, raw=TRUE)))
      
      derivatives <- data.frame(term = rownames(model$coefficients),
                                model$coefficients) %>%
              tidyr::separate("term", c("term","pow"), sep = "[)]", remove = TRUE, fill = "left") 

        args <- "X"
        
        derivative_strings <- derivatives %>%
                mutate(pow = as.numeric(pow),
                       pow_1st = ifelse(pow - 1 >= 0, pow - 1, NA),
                       pow_2nd = ifelse(pow - 2 >= 0, pow - 2, NA),
                       fx_term = ifelse(is.na(pow),paste0(Estimate),
                              ifelse(pow > 0,paste0(Estimate, " * X**",pow),
                                            paste0(Estimate))),
                       df_dx_term = ifelse(pow_1st == 0,paste0(Estimate),
                                    ifelse(pow_1st > 0,paste0(pow * Estimate, " * X**",pow_1st), NA))
                       #df2_dx_term = ifelse(pow_2st >= 0 0,paste0(pow * Estimate, " * X**",pow_1st), NA)
                       )
        
        ## Create function f(x,y)
        function_str <- derivative_strings %>% select(fx_term) %>% na.omit() %>% group_by() %>% summarise(f = paste0(fx_term, collapse = " + "))
        eval(parse(text = paste('f_xy <- function(', args, ') { return(' , function_str , ')}', sep='')))
        
        ## Create function df/dx
        function_df_dx <- derivative_strings %>% select(df_dx_term) %>% na.omit() %>% group_by() %>% summarise(df_dx = paste0(df_dx_term, collapse = " + "))
        eval(parse(text = paste('df_dx <- function(', args, ') { return(' , function_df_dx , ')}', sep='')))
        

    
        game_ratings_scored <- game_ratings() %>%
              mutate(ModelElo = f_xy(GameNumber),
                     RateChange = df_dx(GameNumber)
                     )
        
        return(game_ratings_scored)
      
})

# team_col <- team_day_ratings_team %>% select(team) %>% distinct()
# 
# team_col$col <- rep(1:6, times=500)[1:nrow(team_col)]
# 
# team_max_min_plot <- team_day_ratings_team %>%
#        filter(!is.na(class)) %>%
#         left_join(team_col, by = "team") %>%
#         ggplot(aes(x=date, y=EloRating, fill=as.factor(col), color=as.factor(col), label=paste0(team,"\n",date))) +
#         geom_hline(yintercept = 1500, color = "grey50", size = 3, alpha = 0.7) +
#         #geom_line(size = 2, alpha = 0.9) +
#         geom_point(size = 3) +
#         ggrepel::geom_label_repel(color = "grey90") + 
#         theme_standard() + ggthemes::scale_fill_gdocs() + ggthemes::scale_color_gdocs() +
#         labs(title = paste0("Team Peaks and Valleys, 1997-2018\n@crowdscoutsprts (crowdscoutsports.com/team_elo.php)"),
#              x="Date",
#              y="Elo Rating") +
#         guides(color = FALSE, fill = FALSE)
#   
# ggsave(filename = paste0("/Users/colander1/Downloads/team_max_min_plot.png"), plot = team_max_min_plot, height = 11, width = 16)

```

Sidebar {.sidebar}
=====================================

## Select Inputs

```{r}

output$team_input <- renderUI({
    
    teams <- c('ANA',	'ARI',	'BOS',	'BUF',	'CAR',	'CBJ',	'CGY',	'CHI',	'COL',	'DAL',	'DET',	'EDM',	'FLA',	'LAK',	'MIN',	'MTL',	'NJD',	'NSH',	'NYI',	'NYR',	'OTT',	'PHI',	'PIT',	'SJS',	'STL',	'TBL',	'TOR',	'VAN',	'VGK',	'WPG',	'WSH')


    selectizeInput("team", "Select Team(s): ",
                  c(teams),
                  multiple = FALSE,
                  selected = "WSH"
                  )
})

uiOutput("team_input")

```

Increasing the polynomial degree increases the complexity of the modeled team rating over time.


```{r}
output$poly_input <- renderUI({

  inputPanel(
  sliderInput("poly_degree","Polynomial Degree:", min = 2, max = 20, step = 1, value = 10)
  )
})

uiOutput("poly_input")  

```

Team Elo Over Time
============================================================================

Row {data-height=500}
-------------------------------------

### Team Rating By Game

```{r}

renderPlotly({

team_abb <- input$team

team_plot <- ggplot() +
        geom_line(data = team_day_ratings, aes(x=GameNumber, y=EloRating), color = "grey50", alpha = 0.1) +
        geom_hline(yintercept = 1500, color = "grey50", size = 3, alpha = 0.7) +
        geom_point(data = game_ratings_scored(), aes(x=GameNumber, y=EloRating, color = Season), size = 3, alpha = 0.3) +
        geom_line(data = game_ratings_scored(), aes(x=GameNumber, y=ModelElo), color = "grey20", size = 3, alpha = 0.8) +
        #ggrepel::geom_label_repel(data = game_ratings_scored(), aes(x=GameNumber, y=EloRating, label=ifelse(!is.na(class), paste0(team,"\n",date), NA)), color = "grey90") +
        theme_standard() + ggthemes::scale_fill_gdocs() + ggthemes::scale_color_gdocs() +
        labs(title = paste0(team_abb," Team Elo Rating, 1997-2018\n@crowdscoutsprts (crowdscoutsports.com/team_elo.php)"),
             x="Game Number",
             y="Elo Rating",
             color = "Season") +
        guides(color = FALSE, fill = FALSE)

  a <- ggplotly(team_plot, height = 500, width = 1600) %>%
            layout(showlegend = FALSE)

  a
})

```

Row {data-height=500}
-------------------------------------

### Rate of Change of Team Strength
The rate of change of team strength is the first order derivative of the modeled team strength (as a function of game number, grey line above), conveying if a team is getting better or worse at any given point in time. Where the rate crosses the x=0 axis signifies bottoming out or maxing out.

```{r}

renderPlotly({

team_abb <- input$team

team_plot <- ggplot() +
        geom_hline(yintercept = 0, color = "grey50", size = 3, alpha = 0.7) +
        geom_line(data = game_ratings_scored(), aes(x=GameNumber, y=RateChange, color = Season), size = 3, alpha = 0.8) +
        #ggrepel::geom_label_repel(data = game_ratings_scored(), aes(x=GameNumber, y=EloRating, label=ifelse(!is.na(class), paste0(team,"\n",date), NA)), color = "grey90") +
        theme_standard() + ggthemes::scale_fill_gdocs() + ggthemes::scale_color_gdocs() +
        labs(title = paste0(team_abb," Team Trends, 1997-2018\n@crowdscoutsprts (crowdscoutsports.com/team_elo.php)"),
             x="Game Number",
             y="Rate of Change",
             color = "Season") +
        guides(color = FALSE, fill = FALSE)

  a <- ggplotly(team_plot, height = 500, width = 1600) %>%
            layout(showlegend = FALSE)

  a
})

```
