---
title: "Gradient Ascent and Goal Scoring"
resource_files:
- goal_surface_df_combos.csv
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}

library(plotly); library(dplyr); library(ggplot2); library(shiny)

fun.draw_rink <- function() {
    
    xseq <- seq(-4, 4, length = 100)
    theta1 <- seq(0, 2 * pi, length = 300)
    theta <- seq(0, 2 * pi, length = 300)
    dd <- (5 + 7 / 12) / 2
    
    ## Blank NHL Rink
    
    rink <- ggplot(data = data.frame(x = 1, y = 1), aes(x, y)) + 
        
    geom_path(data = data.frame(
        x = c(15, 87 + 13 * sin(seq(0, pi / 2, length = 20)), 
            87 + 13 * sin(seq(pi / 2, 0, length = 20)), 15), 
        y = c(-42.5, -42.5 + 15 - 15 * cos(seq(0, pi / 2, length = 20)), 
            42.5 - 15 + 15 * cos(seq(pi / 2, 0, length = 20)), 42.5))) + 
    # geom_path(data = data.frame(
    #     x = c(15, -87 - 13 * sin(seq(0, pi / 2, length = 20)), 
    #         -87 - 13 * sin(seq(pi / 2, 0, length = 20)), 15), 
    #     y = c(-42.5, -42.5 + 15 - 15 * cos(seq(0, pi / 2, length = 20)), 
    #         42.5 - 15 + 15 * cos(seq(pi / 2, 0, length = 20)), 42.5))) + 
    ## Goal Lines
    geom_path(data = data.frame(x = c(89),
                                y = c(42.5 - 15 + sqrt(15^2 - (15 - 11)^2), 
                                    -(42.5 - 15 + sqrt(15^2 - (15 - 11)^2)))), 
              color = 'red') + 
    # geom_path(data = data.frame(x = c(-89), 
    #                             y = c(42.5 - 15 + sqrt(15^2 - (15 - 11)^2), 
    #                                 -(42.5 - 15 + sqrt(15^2 - (15 - 11)^2)))), 
    #           color = 'red') +
    ## Nets
    geom_path(data = data.frame(x = c(90, 92, 92, 90)), y = c(-3, -3, 3, 3)) + 
    # geom_path(data = data.frame(x = c(-90, -92, -92, -90), y = c(-3,-3, 3, 3))) +
    
    ## Restricted Area
    geom_segment(aes(x = 89, y = -11, xend = 100, yend = -14), color = 'red') + 
    geom_segment(aes(x = 89, y = 11, xend = 100, yend = 14), color = 'red') + 
    #geom_segment(aes(x = -89, y = -11, xend = -100, yend = -14), color = 'red') + 
    #geom_segment(aes(x = -89, y = 11, xend =-100, yend = 14), color = 'red') +
        
    ## Red Line (Center Ice)
    #geom_segment(aes(x = 0, y = -42.5, xend = 0, yend = 42.5), color = 'red', size = 1) +
    
    ## Blue Lines
    geom_segment(aes(x = 25, y = -42.5, xend = 25,  yend = 42.5), color = 'blue', size = 1) + 
    #geom_segment(aes(x = -25, y = -42.5, xend = -25,  yend = 42.5), color = 'blue', size = 1) +
        
    ## Crease
    geom_polygon(data = data.frame(x = 1 * c(89, 83+xseq^2 / 4^2 * 1.5, 89),
                                   y = c(-4, xseq, 4)), 
                 color = 'red', fill = 'deepskyblue2') + 
    #geom_polygon(data = data.frame(x = -1 * c(89, 83 + xseq^2 / 4^2 * 1.5, 89),
    #                               y = c(-4, xseq, 4)), 
    #             color = 'red', fill = 'deepskyblue2') +

    ## Center Ice Circle
    #geom_path(data = data.frame(x = 15 * sin(theta1)), 
    #          y = 15 * cos(theta1), color = 'deepskyblue2') +
        
    ## Faceoff Dots
    #geom_polygon(data = data.frame(y = 22 + 1 * cos(theta), 
    #                               x = 20 + 1 * sin(theta)), 
    #             color = "red", fill = "red") + 
    #geom_polygon(data = data.frame(y = 22 + 1 * cos(theta), 
    #                               x = -20 + 1 * sin(theta)), 
    #             color = "red", fill = 'red') + 
    #geom_polygon(data = data.frame(y = -22 + 1 * cos(theta), 
    #                               x = -20 + 1 * sin(theta)), 
    #             color = 'red', fill = 'red') + 
    #geom_polygon(data = data.frame(y = -22 + 1 * cos(theta), 
    #                               x = 20 + 1 * sin(theta)), 
    #             color = 'red', fill = 'red') + 
    #geom_polygon(data = data.frame(y = 22 + 1 * cos(theta), 
    #                               x = -69 + 1 * sin(theta)), 
    #             color = 'red', fill = 'red') + 
    geom_polygon(data = data.frame(y = 22 + 1 * cos(theta), 
                                   x = 69 + 1 * sin(theta)), 
                 color = 'red', fill = 'red') + 
    #geom_polygon(data = data.frame(y = -22 + 1 * cos(theta), 
    #                               x = -69 + 1 * sin(theta)), 
    #             color = 'red', fill = 'red') + 
    geom_polygon(data = data.frame(y = -22 + 1 * cos(theta), 
                                   x = 69 + 1 * sin(theta)), 
                 color = 'red', fill = 'red') +

    ## Faceoff Circles
    geom_segment(aes(y = 22 - 0.75, x = 69 - 2, 
                     yend = 22 - 0.75, xend = 69 - 6), color = 'red') + 
    geom_segment(aes(y = 22 + 0.75, x = 69 - 2, 
                     yend = 22 + 0.75, xend = 69 - 6), color = 'red') + 
    geom_segment(aes(y = 22 + 0.75, x = 69 + 2, 
                     yend = 22 + 0.75, xend = 69 + 6), color= 'red') + 
    geom_segment(aes(y = 22 - 0.75, x = 69 - 2, 
                     yend = 22 - 0.75, xend = 69 - 6), color = 'red') + 
    geom_segment(aes(y = -22 + 0.75, x = 69 - 2, 
                     yend = -22 + 0.75, xend = 69 - 6), color= 'red') + 
    geom_segment(aes(y = -22 + 0.75, x = 69 + 2, 
                     yend = -22 + 0.75, xend = 69 + 6), color= 'red') + 
    geom_segment(aes(y = -22 - 0.75, x = 69 - 2, 
                     yend = -22 - 0.75, xend = 69 - 6), color = 'red') + 
    geom_segment(aes(y = -22 - 0.75, x = 69 + 2, 
                     yend = -22 - 0.75, xend = 69 + 6), color = 'red') + 
    geom_segment(aes(y = 22 - 0.75, x = 69 + 2, 
                     yend = 22 - 0.75, xend = 69 + 6), color = 'red') + 
    #geom_segment(aes(y = 22 + 0.75, x = -69 - 2, 
    #                 yend = 22 + 0.75, xend = -69 - 6), color = 'red') + 
    #geom_segment(aes(y = 22 - 0.75, x = -69 - 2, 
    #                 yend = 22 - 0.75, xend = -69 - 6), color = 'red') + 
    #geom_segment(aes(y = 22 + 0.75, x = -69 + 2, 
    #                 yend = 22 + 0.75, xend = -69 + 6), color = 'red') + 
    #geom_segment(aes(y = -22 + 0.75, x = -69 - 2, 
    #                 yend = -22 + 0.75, xend = -69 - 6), color = 'red') + 
    #geom_segment(aes(y = 22 - 0.75, x = -69 + 2, 
    #                 yend = 22 - 0.75, xend = -69 + 6), color = 'red') + 
    #geom_segment(aes(y = -22 + 0.75, x = -69 + 2, 
    #                 yend = -22 + 0.75, xend = -69 + 6), color= 'red') + 
    #geom_segment(aes(y = -22 - 0.75, x = -69 - 2, 
    #                 yend = -22 - 0.75, xend = -69 - 6), color = 'red') + 
    #geom_segment(aes(y = -22 - 0.75, x = -69 + 2, 
    #                 yend = -22 - 0.75, xend = -69 + 6), color = 'red') + 
    geom_segment(aes(y = 22 - 15, x = 69 - dd, 
                     yend = 22 - 17, xend = 69 - dd), color = 'red') + 
    geom_segment(aes(y = 22 - 15, x = 69 + dd, 
                     yend = 22 - 17, xend = 69 + dd), color = 'red') + 
    geom_segment(aes(y = 22 + 15, x = 69 + dd, 
                     yend = 22+17, xend = 69 + dd), color = 'red') + 
    geom_segment(aes(y = 22 + 15, x = 69 - dd, 
                     yend = 22 + 17, xend = 69 - dd), color = 'red') + 
    geom_segment(aes(y = -22 + 15, x = 69 - dd, 
                     yend = -22 + 17, xend = 69 - dd), color = 'red') + 
    geom_segment(aes(y = -22 + 15, x = 69 + dd, 
                     yend = -22 + 17, xend = 69 + dd), color = 'red') + 
    geom_segment(aes(y = -22 - 15, x = 69 - dd, 
                     yend = -22 - 17, xend = 69 - dd), color= 'red') + 
    geom_segment(aes(y = -22 - 15, x = 69 + dd, 
                     yend = -22 - 17, xend = 69 + dd), color = 'red') + 
    #geom_segment(aes(y = -22 + 15, x = -69 + dd, 
    #                 yend = -22 + 17, xend = -69 + dd), color = 'red') + 
    #geom_segment(aes(y = -22 - 15, x = -69 - dd, 
    #                 yend = -22 - 17, xend = -69 - dd), color = 'red') + 
    #geom_segment(aes(y = -22 - 15, x = -69 + dd, 
    #                 yend = -22 - 17, xend = -69 + dd), color = 'red') + 
    #geom_segment(aes(y = -22 + 15, x = -69 - dd, 
    #                 yend = -22 + 17, xend = -69 - dd), color = 'red') + 
    #geom_segment(aes(y = 22 - 15, x = -69 + dd, 
    #                 yend = 22 - 17, xend = -69 + dd), color = 'red') + 
    #geom_segment(aes(y = 22 - 15, x = -69 - dd, 
     #                yend = 22 - 17, xend = -69 - dd), color = 'red') + 
    #geom_segment(aes(y = 22 + 15, x = -69 - dd, 
    #                 yend = 22 + 17, xend = -69 - dd), color = 'red') + 
    #geom_segment(aes(y = 22 + 15, x = -69 + dd, 
    #                 yend = 22 + 17, xend = -69 + dd), color = 'red') + 
    geom_segment(aes(y = 22 + 0.75, x = 69 + 2, 
                     yend = 22 + 3.75, xend = 69 + 2), color = 'red') + 
    geom_segment(aes(y = 22 + 0.75, x = 69 - 2, 
                     yend = 22 + 3.75, xend = 69 - 2), color = 'red') + 
    geom_segment(aes(y = 22 - 0.75, x = 69 + 2, 
                     yend = 22 - 3.75, xend = 69 + 2), color = 'red') + 
    geom_segment(aes(y = 22 - 0.75, x = 69 - 2, 
                     yend = 22 - 3.75, xend = 69 - 2), color = 'red') + 
    #geom_segment(aes(y = 22 + 0.75, x = -69 + 2, 
    #                 yend = 22 + 3.75, xend = -69 + 2), color = 'red') + 
    #geom_segment(aes(y = 22 + 0.75, x = -69 - 2, 
    #                 yend = 22 + 3.75, xend = -69 - 2), color = 'red') + 
    #geom_segment(aes(y = 22 - 0.75, x = -69 + 2, 
    #                 yend = 22 - 3.75, xend = -69 + 2), color = 'red') + 
    #geom_segment(aes(y = 22 - 0.75, x = -69 - 2, 
    #                 yend = 22 - 3.75, xend = -69 - 2), color = 'red') + 
    #geom_segment(aes(y = -22 - 0.75, x = -69 + 2, 
    #                 yend = -22 - 3.75, xend = -69 + 2), color = 'red') + 
    #geom_segment(aes(y = -22 - 0.75, x = -69 - 2, 
    #                 yend = -22 - 3.75, xend = -69 - 2), color = 'red') + 
    #geom_segment(aes(y = -22 + 0.75, x = -69 + 2, 
    #                 yend = -22 + 3.75, xend = -69 + 2), color = 'red') + 
    #geom_segment(aes(y = -22 + 0.75, x = -69 - 2, 
    #                 yend = -22 + 3.75, xend = -69 - 2), color = 'red') + 
    geom_segment(aes(y = -22 + 0.75, x = 69 + 2, 
                     yend = -22 + 3.75, xend = 69 + 2), color = 'red') + 
    geom_segment(aes(y = -22 - 0.75, x = 69 - 2, 
                     yend = -22 - 3.75, xend = 69 - 2), color = 'red') + 
    geom_segment(aes(y = -22 + 0.75, x = 69 - 2, 
                     yend = -22 + 3.75, xend = 69 - 2), color = 'red') + 
    geom_segment(aes(y = -22 - 0.75, x = 69 + 2, 
                     yend = -22 - 3.75, xend = 69 + 2), color = 'red') + 
    geom_path(data = data.frame(y = 22 + 15 * cos(theta), 
                                x = 69 + 15 * sin(theta)), color = 'red') + 
    #geom_path(data = data.frame(y = 22 + 15 * cos(theta), 
    #                            x = -69 + 15 * sin(theta)), color = 'red') + 
    #geom_path(data = data.frame(y = -22 + 15 * cos(theta), 
    #                            x = -69 + 15 * sin(theta)), color = 'red') + 
    geom_path(data = data.frame(y = -22 + 15 * cos(theta), 
                                x = 69 + 15 * sin(theta)), color = 'red') + 
        
    theme_void()
}

rink <- fun.draw_rink() + coord_fixed()

#load("~/Documents/CWA/Hockey Data/scored_data.RData")
# 
# goal_surface_df <- scored_data %>%
#       filter(p1_name == "ALEX OVECHKIN") %>%
#       filter(EmptyNet_SA == 0) %>%
#       mutate(Game_State = ifelse(Shooter_State > Goalie_State, "PP","Non-PP"),
#              Shooting_Team = ifelse(Ev_Team == Home_Team, as.character(Home_Team), as.character(Away_Team))) %>%
#       group_by(Game_State, Shooter_Handedness, Shooting_Team, X, Y) %>%
#       summarise(Shots = n(),
#                 Goals = sum(Goal),
#                 Goal_Prob = mean(Goal),
#                 Share_OZone = mean(ifelse(Ev_Zone == "Off",1,0))) %>%
#       filter(Share_OZone > 0.9) %>%
#       filter(Shooter_Handedness != "U") %>%
#       ungroup()
# 
# write.csv(goal_surface_df, "~/Downloads/goal_surface_df_combos.csv", row.names = FALSE)

library(knitr)

goal_df <- reactive({
  
  teams <- input$teams
  handedness <- input$handed
  state <- input$state
  
  round_param <- input$round_param
  
  goal_surface_df <- read.csv("goal_surface_df_combos.csv")

  goal_df <- goal_surface_df %>% 
        filter(Shooting_Team %in% teams) %>%
        filter(Shooter_Handedness %in% handedness) %>%
        filter(Game_State %in% state) %>%
    
        filter(X > 25) %>% ## Offensive zone shots only
        ungroup() %>%
        mutate(X = as.double(round_param * floor(X / round_param)),
               Y = as.double(round_param * floor(Y / round_param)),
               Shots = as.double(Shots),
               Goals = as.double(Goals)
               ) %>%
        group_by(X, Y) %>%
        summarise(Goal_Prob = sum(Goals, na.rm=T) / sum(Shots, na.rm = T),
                  Sample =  sum(Shots, na.rm = T)) %>%
        ungroup() %>%
        mutate(X = as.double(X),
               Y = as.double(Y),
               Goal_Prob = as.double(Goal_Prob)) %>%
        filter(Sample > 10) ## Remove low volume shooting locations
        
  
  return(goal_df)
        
})


goal_function_surface <- reactive({
        
        poly_degree <- input$poly_degree
        
        model <- summary(lm(data = goal_df(), Goal_Prob ~ poly(X,Y, degree = poly_degree, raw=TRUE)))

        derivatives <- data.frame(term = rownames(model$coefficients),
                                  model$coefficients) %>%
                tidyr::separate("term", c("term","pow"), sep = "[)]", remove = TRUE, fill = "left") %>%
                tidyr::separate("pow", c("X_pow","Y_pow"), sep = "[.]", remove = TRUE, fill = "left")
        
        args <- "X, Y"
        
        derivative_strings <- derivatives %>%
                mutate(X_pow = as.numeric(X_pow),
                       Y_pow = as.numeric(Y_pow),
                       X_pow_prime = X_pow - 1,
                       Y_pow_prime = Y_pow - 1,
                       fx_term = ifelse(is.na(X_pow) | is.na(Y_pow),paste0(Estimate),
                              ifelse(X_pow > 0 & Y_pow > 0,paste0(Estimate, " * X**",X_pow, " * Y**",Y_pow),
                              ifelse(X_pow > 0 ,paste0(Estimate, " * X**",X_pow),   
                              ifelse(Y_pow > 0 ,paste0(Estimate, " * Y**",Y_pow),
                                            paste0(Estimate))))),
                       df_dx_term = ifelse(X_pow_prime >= 0 & Y_pow > 0,paste0(X_pow * Estimate, " * X**",X_pow_prime," * Y**",Y_pow),
                               ifelse(X_pow_prime >= 0,paste0(X_pow * Estimate, " * X**",X_pow_prime),
                                      NA)),
                       df_dy_term = ifelse(Y_pow_prime >= 0 & X_pow > 0,paste0(Y_pow * Estimate, " * Y**",Y_pow_prime," * X**",X_pow),
                               ifelse(Y_pow_prime >= 0,paste0(Y_pow * Estimate, " * Y**",Y_pow_prime),
                                      NA))
                       
                       )
        
        ## Create function f(x,y)
        function_str <- derivative_strings %>% select(fx_term) %>% na.omit() %>% group_by() %>% summarise(f = paste0(fx_term, collapse = " + "))
        eval(parse(text = paste('f_xy <- function(', args, ') { return(' , function_str , ')}', sep='')))
        
        ## Create function df/dx
        function_df_dx <- derivative_strings %>% select(df_dx_term) %>% na.omit() %>% group_by() %>% summarise(df_dx = paste0(df_dx_term, collapse = " + "))
        eval(parse(text = paste('df_dx <- function(', args, ') { return(' , function_df_dx , ')}', sep='')))
        
        ## Create function df/dy
        function_df_dy <- derivative_strings %>% select(df_dy_term) %>% na.omit() %>% group_by() %>% summarise(df_dy = paste0(df_dy_term, collapse = " + "))
        eval(parse(text = paste('df_dy <- function(', args, ') { return(' , function_df_dy , ')}', sep='')))
        
    
        goal_function_surface <- goal_df() %>%
              mutate(f = f_xy(X, Y),
                     dfdx = df_dx(X, Y),
                     dfdy = df_dy(X, Y),
                     X_end = X + (dfdx*30),
                     Y_end = Y + (dfdy*30)
                     )

  return(goal_function_surface)         
        
})


predicted_goal_prob_mat <- reactive({
  
        poly_degree <- input$poly_degree
        
        model <- lm(data = goal_df(), Goal_Prob ~ poly(X,Y, degree = poly_degree, raw=TRUE))

        predicted <- as.data.frame(predict(model, goal_df()))
        colnames(predicted) <- "predicted"
      
      
        predicted_goal_prob_mat <- goal_df() %>%
            bind_cols(predicted) %>% 
            data.table::dcast(X ~ Y, value.var = "predicted") %>%
            select(-c(X)) %>%
            as.matrix()
      
        return(predicted_goal_prob_mat)
  
})


```

Sidebar {.sidebar}
=====================================

### Shooting Inputs

```{r}

output$team_input <- renderUI({
    
    teams <- c('ANA',	'ARI',	'BOS',	'BUF',	'CGY',	'CAR',	'CHI',	'COL',	'CBJ',	'DAL',	'DET',	'EDM',	'FLA',	'L.A',	'MIN',	'MTL',	'NSH',	'N.J',	'NYI',	'NYR',	'OTT',	'PHI',	'PIT',	'S.J',	'STL',	'T.B',	'TOR',	'VAN',	'VGK',	'WSH',	'WPG')


    selectizeInput("teams", "Select Team(s): ",
                  c(teams),
                  multiple = TRUE,
                  selected = "WSH"
                  )
})


output$handed_input <- renderUI({

    handed <- c("L","R")
    
    selectizeInput("handed", "Shooter Handedness: ",
                  c(handed),
                  multiple = TRUE,
                  selected = c(handed)
                  )

})

output$state_input <- renderUI({

    state <- c("PP","Non-PP")

    selectizeInput("state", "Select Game State(s): ",
                  c(state),
                  multiple = TRUE,
                  selected = c(state)
                  )

})

uiOutput("team_input")
uiOutput("handed_input")
uiOutput("state_input")

```

### Model Inputs

Increasing the polynomial degree increases the complexity of the modeled goal probability and subsequent gradient.

```{r}
output$poly_input <- renderUI({

  inputPanel(
  sliderInput("poly_degree","Polynomial Degree:", min = 3, max = 20, step = 1, value = 10)
  )
})

uiOutput("poly_input")  

```

Coordinate rounding parameter is used to group coordinates in order to increase sample size. When limiting to a team shooting right handed on the PP, for example, a higher parameter would help create a smoothed surface.

```{r}

output$round_param <- renderUI({

  inputPanel(
  sliderInput("round_param","Coordinate Rounding Parameter:", min = 3, max = 8, step = 1, value = 5)
  )
})

uiOutput("round_param")  

```

Goal Gradient Map
============================================================================

Row {data-height=125}
-------------------------------------

### Overview

My previous work including the [math and logic behind this analysis can be found here.](https://crowdscoutsports.shinyapps.io/GoalGradientAscent/)
The plots below calculate situational goal probability by some combination of team, shooter handedness, and strength. 

* Observed Goal Probability Map - the probability of goal from each set of coordinates in the offensive zone (grouped together with coordinate rounding parameter)
* Modeled Goal Probability Map - creating a function to represent the goal probability, a higher polynomial degree creates more complexity in the surface (potentially causing some stranges things to happen)
* Modeled Gradient Ascent Map - based on modeled goal surface, the direction where goal probability increases the most from an given point in the offensive zone
* Modeled Contour Map - a 2D representation of the Modeled Goal Probability Map


Row {data-height=300}
-------------------------------------

### Observed Goal Probability Map

```{r probs, echo=FALSE}

renderPlotly({
  

Goal_Prob_mat <- goal_df() %>% 
            data.table::dcast(X ~ Y, value.var = "Goal_Prob") %>%
            select(-c(X)) %>%
            as.matrix()

plotly::plot_ly(
                     z = Goal_Prob_mat,
                     colors = "YlOrRd"
                     #direction = -1
                     ) %>%
          add_surface() %>%
          layout(
              title = paste0("Observed Goal Probability Map\n",
                             paste(input$teams,sep="", collapse="-"),"; ",
                             paste(input$handed,sep="", collapse="-"),"; ",
                             paste(input$state,sep="", collapse="-")
                    )
              )

})

```

### Modeled Goal Probability Map

```{r}

renderPlotly({
  
    plotly::plot_ly( z = predicted_goal_prob_mat(),
                 colors = "YlOrRd"
                ) %>%
          add_surface() %>%
          layout(
              title = paste0("Modeled Goal Probability Map\n",
                             paste(input$teams,sep="", collapse="-"),"; ",
                             paste(input$handed,sep="", collapse="-"),"; ",
                             paste(input$state,sep="", collapse="-")
                    )
              )

})


```

Row {data-height=550}
-------------------------------------

### Modeled Gradient Ascent Map

```{r, gradmap, echo=FALSE}

renderPlot({
  
goal_grad_contour <- rink +
    #geom_contour(data = goal_df(), aes(x=X, y=Y, z=Goal_Prob, colour = calc(level)), bins = 8) +
    #scale_color_gradient2(low="#4575b4", mid = "#74add1", high="#d73027", labels = scales::percent, limits = c(0, NA)) +
    geom_segment(data = goal_function_surface(), aes(x=X, xend=X_end, y=Y, yend=Y_end), position = "identity", color = "grey25",
                 arrow=arrow(length = unit(0.5, "cm"))
                 ) +
    xlim(c(15,100)) +
    ylim(c(-45,45)) +
    labs(color = "Shooting %",
         title = paste0("Goal Probability Gradient Ascent Map\n",
                    paste(input$teams,sep="", collapse="-"),"; ",
                             paste(input$handed,sep="", collapse="-"),"; ",
                             paste(input$state,sep="", collapse="-")))


 #goal_grad_contour <- ggplotly(goal_grad_contour, source = 'source', tooltip = "text")

  goal_grad_contour



}, height = 600, width = 600)


```

### Modeled Contour Map

```{r, contour, echo=FALSE}

renderPlot({
  
goal_grad_contour <- rink +
    geom_contour(data = goal_df(), aes(x=X, y=Y, z=Goal_Prob, colour = calc(level)), bins = 8) +
    scale_color_gradient2(low="#4575b4", mid = "#74add1", high="#d73027", labels = scales::percent, limits = c(0, NA)) +
    
    #geom_segment(data = goal_function_surface(), aes(x=X, xend=X_end, y=Y, yend=Y_end), position = "identity", color = "grey25",
    #             arrow=arrow(length = unit(0.5, "cm"))
    #             ) +
    labs(color = "Shooting %",
         title = paste0("Goal Probability Contour Map\n",
                    paste(input$teams,sep="", collapse="-"),"; ",
                             paste(input$handed,sep="", collapse="-"),"; ",
                             paste(input$state,sep="", collapse="-")))


 #goal_grad_contour <- ggplotly(goal_grad_contour, source = 'source', tooltip = "text")

  goal_grad_contour



}, height = 600, width = 600)


```
