
```{r echo=FALSE}
library(ggplot2);library(dplyr); library(DataCombine)
library(glmnet); library(nhlscrapr); library(caret); library(RMySQL); library(readr); library(reshape2); library(rvest)
library(httr); library(data.table); library("reshape2");
library(ggplot2)
library(TeachBayes)
library(xts)
library(RMySQL)
library(DBI)
theme_set(theme_bw())


txt <- element_text(size = 12, colour = "grey25", face = "plain")
bold_txt <- element_text(size = 20, colour = "navy", face = "bold")

theme_standard <- function(base_size = 16, base_family = "") {
  theme_bw(base_size = base_size, base_family = base_family) +
    theme(
      strip.background = element_blank(), 
      
      panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(),
      panel.grid.major.y = element_line( colour = "white", size = 2), 
      panel.grid.major.x = element_line( colour = "white", size = 2), 
      
      panel.background = element_rect(fill="grey90"),
      plot.background = element_rect(fill="grey90"),
      legend.background = element_rect(fill="grey90"),
      legend.key = element_rect(fill="grey90", size = 20),
      legend.key.size = unit(1,"cm"),
      
      panel.border = element_blank(), 
      
      line = element_line( colour = "white", size = 2),
      axis.text.x = element_text(angle = 90, hjust = 1),
      text = txt, 
      plot.title = bold_txt, 
      
      axis.title = txt, 
      axis.text = txt, 
      
      legend.title = bold_txt, 
      legend.text = txt ) 
}

# Multiple plot function
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}


```

# Load Scored Data

```{r}
scored_data2011_2012 <- read.csv("~/Documents/CWA/HockeyScrape/scored_data2011_2012.csv") %>% select(-starts_with("X."))
scored_data2013_2014 <- read.csv("~/Documents/CWA/HockeyScrape/scored_data2013_2014.csv") %>% select(-starts_with("X."))
scored_data2015_2016 <- read.csv("~/Documents/CWA/HockeyScrape/scored_data2015_2016.csv") %>% select(-starts_with("X."))

scored_data <- read.csv("~/Documents/CWA/HockeyScrape/scored_data2017_2018.csv") %>% 
  select(-starts_with("X."), 
         -starts_with("Unna")) %>%
  plyr::rbind.fill(scored_data2011_2012) %>%
  plyr::rbind.fill(scored_data2013_2014) %>%
  plyr::rbind.fill(scored_data2015_2016) %>%
  mutate(xG = xG_raw,
         xG_team = ifelse(is_Rebound == 0, xG_raw,
                          ifelse(is_Rebound == 1 & lag(is_Rebound) == 0, xG_raw * (1-lag(xG_raw)),
                                 ifelse(is_Rebound == 1 & lag(is_Rebound) == 1 & lag(is_Rebound,2) == 0,
                                        xG_raw * (1-lag(xG_raw)) * (1-lag(xG_raw,2)),
                                        ifelse(is_Rebound == 1 & lag(is_Rebound) == 1 & lag(is_Rebound,2) == 1 & lag(is_Rebound,3) == 0,
                                               xG_raw * (1-lag(xG_raw)) * (1-lag(xG_raw,2)) * (1-lag(xG_raw,3)),
                                               ifelse(is_Rebound == 1 & lag(is_Rebound) == 1 & lag(is_Rebound,2) == 1 & lag(is_Rebound,3) == 1 & lag(is_Rebound,4) == 0,
                                                      xG_raw * (1-lag(xG_raw)) * (1-lag(xG_raw,2)) * (1-lag(xG_raw,3)) * (1-lag(xG_raw,4)),
                                                      xG_raw * (1-lag(xG_raw)) * (1-lag(xG_raw,2)) * (1-lag(xG_raw,3)) * (1-lag(xG_raw,4))))))))


rm(scored_data2011_2012, scored_data2013_2014, scored_data2015_2016)

scored_data %>% group_by(season) %>% summarise(xG = sum(xG_team), G = sum(Goal))

```
### 1. Scored Data from 2009-2018 and ready for analysis

```{r}

## Beta Functions
calcBetaMode <- function(aa, bb) { BetaMode <- (aa - 1)/(aa + bb - 2); return(BetaMode); }
calcBetaMean <- function(aa, bb) { BetaMean <- (aa)/(aa + bb); return(BetaMean); }
calcBetaSd   <- function(aa, bb) { BetaSd <- sqrt((aa * bb)/(((aa + bb)^2) * (aa + bb + 1))); return(BetaSd); }

conn <- dbConnect(MySQL(), user='ca_elo_games', password='cprice31!',
                  host='mysql.crowdscoutsports.com', db='nhl_all')
on.exit(dbDisconnect(conn))

goalie_roster <- dbGetQuery(conn, "SELECT distinct upper(playerName) as `SA_Goalie`, playerId as nhl_id, playerHeight as height,  
                            playerShootsCatches as Catches, playerBirthDate as dob FROM `nhl_all`.`hockey_goalies_roster` AS A")


goalie_roster <- goalie_roster %>%
  mutate(SA_Goalie = ifelse(SA_Goalie == "MATTHEW MURRAY","MATT MURRAY",
                            ifelse(SA_Goalie == "OLIE KOLZIG","OLAF KOLZIG",
                                   ifelse(SA_Goalie == "STEPHEN VALIQUETTE","STEVE VALIQUETTE",
                                          ifelse(SA_Goalie == "THOMAS MCCOLLUM","TOM MCCOLLUM",
                                                 ifelse(SA_Goalie == "JEAN-SEBASTIEN AUBIN", "J-SEBASTIEN AUBIN",
                                                        ifelse(SA_Goalie == "ALEXANDER PECHURSKIY","ALEXANDER PECHURSKI",
                                                               as.character(SA_Goalie)))))))) %>%
  unique()


goalie_data_prep <- scored_data %>%
  filter(season != "20072008") %>%
  filter(nchar(as.character(SA_Goalie)) > 0) %>%
  mutate(SA_Goalie = ifelse(SA_Goalie == "STEPHEN VALIQUETTE","STEVE VALIQUETTE",
                            ifelse(SA_Goalie == "THOMAS MCCOLLUM","TOM MCCOLLUM",
                                   ifelse(SA_Goalie == "MATTHEW MURRAY","MATT MURRAY",
                                          as.character(SA_Goalie)))),

         SA_Team = ifelse(Ev_Team == Home_Team, as.character(Away_Team), as.character(Home_Team)),
         NonRebound_Shot = ifelse(is_Rebound == 0, 1, 0),
         xG_FirstShot = ifelse(is_Rebound == 0, xG, 0)) 

rebound_goal_probability <- goalie_data_prep %>% 
  filter(is_Rebound == 1) %>%
  summarise(rebound_goal_probability = sum(Goal) / n())

goalie_shot_level_prep <- goalie_data_prep %>%
  cbind(rebound_goal_probability) %>%
  left_join(goalie_roster, by ="SA_Goalie") %>%
  mutate(Age = round((as.Date(paste0("10/1/",as.numeric(substr(season,1,4))), format = "%m/%d/%Y") - as.Date(dob)) / 365.25,1)) 


save(goalie_shot_level_prep, file="~/Documents/CWA/Hockey Data/goalie_shot_level_prep.RData")
#scored_data %>% filter(season == "20172018" & Game_Id == "20032" & Ev_Team != "BOS") %>% select(Goal, SA_Goalie, Event, Seconds_Elapsed, Period)

#print(dim(goalie_shot_level_prep))
```

## 2. Score Bayes / Rebound Metrics

```{r}

bayes_lift_fun <- function(xG, GA, Shots, prior = 2000, type = "POST") {
  
      beta_a = (1 - (xG / Shots)) * prior
      beta_b = prior - beta_a
      
      # Overall
      likelihood_a = sum(Shots) - sum(GA) + 1  ## Saves + 1
      likelihood_b = sum(GA) + 1  ## Goals + 1
      
      posterior_a = beta_a + (likelihood_a - 1)  ## Success + Beta A
      posterior_b = beta_b +  (likelihood_b - 1)  ## Goals + Beta B

      prior_mean      = calcBetaMean(beta_a, beta_b)
      posterior_mean  = calcBetaMean(posterior_a, posterior_b)

      if(type == "POST") {
          out  = calcBetaMean(posterior_a, posterior_b) - calcBetaMean(beta_a, beta_b)
        } else {
          out = calcBetaMean(likelihood_a, likelihood_b) - calcBetaMean(beta_a, beta_b)
        }

      return(out)
}

bayes_std_fun <- function(xG, GA, Shots, prior = 2000, type = "POST") {
  
  beta_a = (1 - (xG / Shots)) * prior
  beta_b = prior - beta_a
  
  # Overall
  likelihood_a = sum(Shots) - sum(GA) + 1  ## Saves + 1
  likelihood_b = sum(GA) + 1  ## Goals + 1
  
  posterior_a = beta_a + (likelihood_a - 1)  ## Success + Beta A
  posterior_b = beta_b +  (likelihood_b - 1)  ## Goals + Beta B
  
  if(type == "POST") {
    out  = calcBetaSd(posterior_a, posterior_b) 
  } else {
    out = calcBetaSd(likelihood_a, likelihood_b)
  }
  return(out)
  
}  

goalie_season_results <- goalie_shot_level_prep %>%
      group_by(SA_Goalie, season, Age) %>%
      summarise(xG_Lift_100Shots = (sum(xG) - sum(Goal)) / (n() / 100),
              NonRebound_Shots = sum(NonRebound_Shot),
              Shots = n(),
              GA = sum(Goal),
              SvPct = (Shots - sum(Goal)) / Shots, 
              xG_FirstShot = sum(xG_FirstShot),
              xG = sum(xG),
              xRebounds = sum(xR),
              RBA = sum(is_Rebound),
              xG_RB = sum(xR * rebound_goal_probability),
              
              xG_raw = sum(xG),
              xG_xR_Lift_100Shots = (sum(xG_FirstShot + xG_RB) -sum(Goal)) / (sum(NonRebound_Shot) / 100),

              posterior_xG_lift = bayes_lift_fun(xG, sum(Goal), Shots, 2000, type = "POST"),

              posterior_xG_xR_lift = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 2000, type = "POST"),
              
              posterior_2000_std = bayes_std_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 2000, type = "POST")) 

```

##3. Plot Goaltending by Team Season

```{r}

goalies_team_season_plot <- function(szn) {

team_season_plot <- goalie_season_results %>%
    filter(season == szn) %>%
    group_by(SA_Team) %>%
    mutate(Goalie = paste0(sapply(strsplit(as.character(SA_Goalie), ' '), function(x) x[length(x)])),
           Team_posterior_xG_xR_lift = weighted.mean(posterior_xG_xR_lift, w=NonRebound_Shots),
           Rebound_Adj = posterior_xG_lift - posterior_xG_xR_lift ) %>%
    arrange(Team_posterior_xG_xR_lift, posterior_xG_xR_lift) %>%
    ggplot(aes(x=reorder(SA_Team, Team_posterior_xG_xR_lift), y = posterior_xG_xR_lift, group=SA_Goalie, label=Goalie, fill=NonRebound_Shots)) +
    geom_bar(stat="identity", alpha = 0.5, position = "dodge") +
    geom_point(aes(x=reorder(SA_Team, - Team_posterior_xG_xR_lift), y=Team_posterior_xG_xR_lift), size = 12, alpha = 0.25, color = "grey50") +
    geom_text(aes(x=reorder(SA_Team, - Team_posterior_xG_xR_lift), y=Team_posterior_xG_xR_lift, label=SA_Team), size = 4, alpha = 0.8, color = "grey25") +
    geom_text(size = 3, position = position_dodge(width = 1), color = "grey25") +
    scale_fill_gradient2(low="#DC3912",high="#109618", mid="#990099") +
    theme_standard() + #ggthemes::scale_fill_gdocs() +
    coord_flip() +
    scale_y_continuous(labels = scales::percent) +
    labs(x="",y="Posterior Save% Over Expected Save% (2000 Shot Prior) ",fill="Shots Against",
         title=paste0("Team Bayesian Goals Prevented Compared to Average, Adjusted for Rebounds, ",szn," YTD - ",Sys.Date(),"\n@crowdscoutsprts (github.com/C92Anderson/xG-Model)")) +
    theme(legend.position = "bottom",
          panel.grid.major.x = element_line( colour = "white", size = 2))

ggsave(filename=paste0("/Users/colander1/Downloads/goalies_team_season_plot_",szn,".png"), plot=team_season_plot,  width=20, height=12)

return(team_season_plot)
}

#goalies_team_season_plot("20172018")


```

## All Goalies Bayes

```{r}

bayes_lift_seasons <- function(szn) {
  
bayes_lift_data <- goalie_shot_level_prep %>%
      filter(season == szn) %>%
      group_by(SA_Goalie, season, Age) %>%
      summarise(NonRebound_Shots = sum(NonRebound_Shot),
              xG_FirstShot = sum(xG_FirstShot),
              xG_RB = sum(xR * rebound_goal_probability),
              `100 Shots` = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 100),
              `1000 Shots` = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 1000),
              `2000 Shots` = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 2000),
              `3000 Shots` = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 3000)) %>% 
      ungroup() %>%
      arrange(`2000 Shots`) %>%
      mutate(Order = row_number())

bayes_lift_plot <- bayes_lift_data %>%
    select(SA_Goalie, NonRebound_Shots, Order, ends_with(" Shots")) %>%
    melt(id.vars = c("SA_Goalie","NonRebound_Shots","Order")) %>%
    ggplot(aes(x=reorder(SA_Goalie, Order), y = value, color=variable, group=variable, alpha=NonRebound_Shots, size=NonRebound_Shots)) +
    geom_hline(yintercept = 0, color="grey75") +
    geom_point() +
    theme_standard() + ggthemes::scale_color_gdocs() +
    #scale_fill_gradient2(high="#990099",low="#DC3912", mid="grey75", midpoint = median(bayes_lift_data$NonRebound_Shots)) +
    scale_alpha_continuous(range = c(0.4,0.9)) +
    coord_flip() +
    labs(x="Goalie (Sorted by Performance Based on 2000 Shot Prior)",y="Projected Goals Prevented / 100 Shots", size="Non-Rebound\nShots",alpha="Non-Rebound\nShots",
         color="Bayesian Prior\nStrength",
         title=paste0("Bayesian Goals Prevented per 100 Shots Compared to Average, ",szn,"\nAdjusted for Rebounds (https://github.com/C92Anderson/RITHAC-Bayes)")) +
    theme(#legend.position = "top",
          panel.grid.major.y = element_line( colour = "white", size = 2)) +
      scale_y_continuous(labels = scales::percent) 


ggsave(filename="/Users/colander1/Downloads/bayes_lift_plot.png", plot=bayes_lift_plot,  width=12.5, height=16)

}

bayes_lift_seasons("20172018")
```

## Bayes Error Bars


```{r}


bayes_lift_std_seasons <- function(szn) {
  
bayes_lift_data <- goalie_shot_level_prep %>%
      filter(season == szn) %>%
      group_by(SA_Goalie, season, Age) %>%
      summarise(NonRebound_Shots = sum(NonRebound_Shot),
              xG_FirstShot = sum(xG_FirstShot),
              xG_RB = sum(xR * rebound_goal_probability),
              Likelihood_Lift = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 1500, type = "LKL"),
              Likelihood_Std = 2 * bayes_std_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 1500, type = "LKL"),

              Bayes100_Lift = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 100, type = "POST"),
              Bayes100_Std = 2 * bayes_std_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 100, type = "POST"),

              `275 Shots_Lift` = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 275, type = "POST"),
              `275 Shots_Std` = 2 * bayes_std_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 275, type = "POST"),
              
              Bayes1000_Lift = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 1000, type = "POST"),
              Bayes1000_Std = 2 * bayes_std_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 1000, type = "POST"),

              `1500 Shots_Lift` = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 1500, type = "POST"),
              `1500 Shots_Std` = 2 * bayes_std_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 1500, type = "POST"),
              
              Bayes2000_Lift = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 2000, type = "POST"),
              Bayes2000_Std = 2 * bayes_std_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 2000, type = "POST")
              
              ) %>% 
      ungroup() %>%
      filter(NonRebound_Shots > 100)

likelihood_lift_std_plot <- bayes_lift_data %>%
    ggplot(aes(x=reorder(SA_Goalie, Likelihood_Lift), y = Likelihood_Lift, color=NonRebound_Shots, size=NonRebound_Shots)) +
    geom_hline(yintercept = 0, color="grey25") +
    geom_errorbar(aes(ymin=Likelihood_Lift-Likelihood_Std, ymax=Likelihood_Lift+Likelihood_Std), width=.1, position=position_dodge(0.1), alpha=0.85) +
    geom_point(color="grey30", size=8, alpha=0.8) +
    geom_text(color="grey85", size=2, aes(label = paste0(round(Likelihood_Lift,3)*100,"%"))) +
    theme_standard() + #ggthemes::scale_color_gdocs() +
    scale_color_gradient2(high="#990099",low="#DC3912", mid="grey75", midpoint = median(bayes_lift_data$NonRebound_Shots, na.rm = T), na.value = "grey50") +
    coord_flip() +
    labs(x=paste0("Goalie (Sorted by Save Percentage Lift Over Expected)"),y="Save Percentage Lift Over Expected", size="Non-Rebound\nShots",alpha="Non-Rebound\nShots",
         color="Non-Rebound\nShots",
         title=paste0("Save Percentage Lift Over Expected with Uncertainty Range, ",szn,"\nAdjusted for Rebounds (https://github.com/C92Anderson/RITHAC-Bayes)")) +
    theme(#legend.position = "top",
          panel.grid.major.y = element_line( colour = "white", size = 2)) +
      scale_y_continuous(labels = scales::percent) +
      guides(color = FALSE)

ggsave(filename="/Users/colander1/Downloads/likelihood_lift_std_plot.png", plot=likelihood_lift_std_plot,  width=12.5, height=19)



bayes_lift_std_plot <- bayes_lift_data %>%
    select(SA_Goalie, NonRebound_Shots, starts_with("275"), starts_with("1500")) %>%
    melt(id.vars = c("SA_Goalie","NonRebound_Shots")) %>%
    mutate(Var = paste0(sapply(strsplit(as.character(variable), '_'), function(x) x[1])),
           Class2 = paste0(sapply(strsplit(as.character(variable), '_'), function(x) x[length(x)]))) %>%
    dcast(SA_Goalie + NonRebound_Shots + Var ~ Class2) %>%
    ggplot(aes(x=reorder(SA_Goalie, Lift), y = Lift, group = Var, color=Var, size=NonRebound_Shots), alpha = 0.5) +
    geom_hline(yintercept = 0, color="grey25") +
    geom_errorbar(aes(ymin=Lift-Std, ymax=Lift+Std), width=.1, position=position_dodge(0.1), alpha=0.4) +
    geom_point(size=8, alpha=0.8) +
    geom_text(color="grey85", size=2, aes(label = paste0(round(Lift,3)*100,"%"))) +
    theme_standard() + ggthemes::scale_color_gdocs() +
    coord_flip() +
    labs(x=paste0("Goalie (Sorted by Save Percentage Lift Over Expected)"),y="Save Percentage Lift Over Expected", size="Non-Rebound\nShots",alpha="Non-Rebound\nShots",
         color="Prior Strength",
         title=paste0("Save Percentage Lift Over Expected with Uncertainty Range, ",szn,"\nAdjusted for Rebounds (https://github.com/C92Anderson/RITHAC-Bayes)")) +
    theme(#legend.position = "top",
          panel.grid.major.y = element_line( colour = "white", size = 2)) +
      scale_y_continuous(labels = scales::percent)


ggsave(filename="/Users/colander1/Downloads/bayes_lift_std_plot.png", plot=bayes_lift_std_plot,  width=12.5, height=19)


}

bayes_lift_std_seasons("20172018")

```

##Scatter Plot of xG / GA

```{r}

xG_scatter_adj_plot <- function(szn) {

xG_scatter_adj_data <- goalie_season_results %>%
    filter(NonRebound_Shots > 1) %>%
    filter(season == szn) %>%
    group_by(SA_Goalie) %>%
    arrange(GA) %>%
    mutate(Goalie = paste0(sapply(strsplit(as.character(SA_Goalie), ' '), function(x) x[length(x)])),
           xG_xR = xG_FirstShot + xG_RB,
           Rebound_Adj = xG_xR - xG_raw) 


xG_scatter_adj_data$col <- rep(1:6, times=500)[1:nrow(xG_scatter_adj_data)]

xG_scatter_adj_plot <- xG_scatter_adj_data %>%  
    ggplot() +
    geom_abline(slope = 1, intercept = 0, color = "grey50") +
    geom_point(aes(x=GA, y = xG_xR, label=Goalie, size=NonRebound_Shots, alpha="xG Adjusted for Rebounds",color=as.factor(col))) +
    geom_point(aes(x=GA, y = xG_raw, size=NonRebound_Shots/2, alpha="Raw xG",color=as.factor(col))) +
    geom_segment(aes(x=GA, xend=GA, y=xG_xR, yend=xG_raw, color=as.factor(col))) +
    ggrepel::geom_label_repel(aes(x=GA, y = xG_xR, label=Goalie, color=as.factor(col))) +
    geom_abline(slope = 1, intercept = 0, color = "grey50") +
    theme_standard() + ggthemes::scale_color_gdocs() +
    labs(x="Actual Goals Against",y="Expected Goals Against",fill="Shots Against", alpha="Measurement\n(Adjusting for Rebounds\nIncreases Predictivity)",
         size="Non-Rebound Shots Against",
         title=paste0("Goals Prevented Above Average, Adjusted for Rebounds, ",szn," YTD - ",Sys.Date(),"\n@crowdscoutsprts (github.com/C92Anderson/xG-Model)")) +
    annotate("text", x=0.3 * max(xG_scatter_adj_data$xG_raw), y=0.9 * max(xG_scatter_adj_data$xG_raw), color="grey50", size=4,
                  label="Rebound Adjustment removes credit for saves made on rebounds\ninstead giving credit to preventing rebounds relative to expected rebounds\nsee: https://github.com/C92Anderson/RITHAC-Bayes") +
    annotate("text", x=0.25 * max(xG_scatter_adj_data$xG_raw), y=0.75 * max(xG_scatter_adj_data$xG_raw), color="grey50",size=5, 
                  label="Outperformed Average") +
    annotate("text", y=0.25 * max(xG_scatter_adj_data$xG_raw), x=0.75 * max(xG_scatter_adj_data$GA), color="grey50", size=5,
                  label="Underperformed Average") +
    theme(panel.grid.major.x = element_line( colour = "white", size = 2),
          panel.grid.major.y = element_line( colour = "white", size = 2)) +
    guides(color=FALSE)

ggsave(filename=paste0("/Users/colander1/Downloads/xG_scatter_adj_plot_",szn,".png"), plot=xG_scatter_adj_plot,  width=18, height=12)

return(xG_scatter_adj_plot)
}

xG_scatter_adj_plot("20172018")

```

### Plot xG Performance Lagging Last 100 Shots

```{r}

xG_scatter_last100_plot <- function(szn) {
 
xG_YTD <- goalie_shot_level_prep %>%
      filter(season == szn) %>%
      group_by(SA_Goalie, season, Age) %>%
      summarise(NonRebound_Shots = sum(NonRebound_Shot),
              Total_Shots = n(),
              GA = sum(Goal),
              xGA = sum(xR * rebound_goal_probability) + sum(xG_FirstShot))
  
xG_scatter_adj_data <- goalie_shot_level_prep %>%
      filter(season == szn) %>%
      inner_join(xG_YTD, by = c("SA_Goalie","season","Age")) %>%
      group_by(SA_Goalie,season, Age) %>%
      mutate(SA = 1,
             Cum_Shot = cumsum(SA)) %>%
      filter(Cum_Shot < (Total_Shots - 99) | (Cum_Shot < 2)) %>%
      summarise(GA_lag = sum(Goal),
                xGA_lag = sum(xR * rebound_goal_probability) + sum(xG_FirstShot)) %>%
    left_join(xG_YTD, by = c("SA_Goalie","season","Age")) %>%
    arrange(GA) %>%
    mutate(Goalie = paste0(sapply(strsplit(as.character(SA_Goalie), ' '), function(x) x[length(x)]))) 


xG_scatter_adj_data$col <- rep(1:6, times=500)[1:nrow(xG_scatter_adj_data)]

xG_scatter_adj_plot <- xG_scatter_adj_data %>%  
    filter(NonRebound_Shots > 0) %>%
    ggplot() +
    geom_abline(slope = 1, intercept = 0, color = "grey50") +
    #geom_point(aes(x=GA, y = xGA, label=Goalie, size=NonRebound_Shots, alpha="Current",color=as.factor(col))) +
    #geom_point(aes(x=GA_lag, y = xGA_lag, size=NonRebound_Shots/2, alpha="100 Shots Prior",color=as.factor(col))) +
    geom_segment(aes(x=GA_lag, xend=GA, y=xGA_lag, yend=xGA, color=as.factor(col)), arrow=arrow()) +
    ggrepel::geom_label_repel(aes(x=GA_lag, y = xGA_lag, label=Goalie, color=as.factor(col))) +
    geom_abline(slope = 1, intercept = 0, color = "grey50") +
    theme_standard() + ggthemes::scale_color_gdocs() +
    labs(x="Actual Goals Against",y="Expected Goals Against",fill="Shots Against", alpha="Measurement\n(Adjusting for Rebounds\nIncreases Predictivity)",
         size="Non-Rebound Shots Against",
         title=paste0("Goals Prevented Above Average, Adjusted for Rebounds, ",szn," YTD - ",Sys.Date(),"\n@crowdscoutsprts (github.com/C92Anderson/xG-Model)")) +
    annotate("text", x=0.3 * max(xG_scatter_adj_data$xGA), y=0.9 * max(xG_scatter_adj_data$xGA), color="grey50", size=4,
                  label="Rebound Adjustment removes credit for saves made on rebounds\ninstead giving credit to preventing rebounds relative to expected rebounds\nsee: https://github.com/C92Anderson/RITHAC-Bayes") +
    annotate("text", x=0.25 * max(xG_scatter_adj_data$xGA), y=0.75 * max(xG_scatter_adj_data$xGA), color="grey50",size=5, 
                  label="Outperformed Average") +
    annotate("text", y=0.25 * max(xG_scatter_adj_data$xGA), x=0.75 * max(xG_scatter_adj_data$GA), color="grey50", size=5,
                  label="Underperformed Average") +
    theme(panel.grid.major.x = element_line( colour = "white", size = 2),
          panel.grid.major.y = element_line( colour = "white", size = 2)) +
    guides(color=FALSE)

ggsave(filename=paste0("/Users/colander1/Downloads/xG_scatter_last100_plot_",szn,".png"), plot=xG_scatter_adj_plot,  width=18, height=12)

return(xG_scatter_adj_plot)
}

xG_scatter_last100_plot("20172018")

```

### Plot Performance by Cumulative Shot

```{r}

QREAM_bygame_fun <- function(goalie, seasons=c("20072008","20082009","20092010","20102011","20112012",
                                        "20122013","20132014","20142015","20152016","20162017","20172018"), shot_cut=100) {
  
  library(dplyr)
  
  # Select Goalies, Order by season, game, shot
  all_goalie_games <- goalie_data_prep %>%
    filter(season %in% seasons) %>%
    group_by(SA_Goalie, season,  season2, Game_Id) %>%
    summarise(xG = sum(sum(xG_FirstShot) + ((sum(xR) * 0.26))),
              #xG = sum(xG),
              GA = sum(Goal),
              SA = sum(ifelse(is_Rebound == 0, 1, 0))) %>%
    group_by(SA_Goalie) %>%
    mutate(cum_xG = cumsum(xG),
           cum_GA = cumsum(GA),
           cum_SA = cumsum(SA),
           cum_xG_Lift = cum_xG - cum_GA)
  
  all_goalie_starts <- all_goalie_games %>% group_by(SA_Goalie) %>% top_n(1, -cum_SA) %>%
    mutate(cum_xG = 0,
           cum_GA = 0,
           cum_SA = 0,
           cum_xG_Lift = 0) %>%
    bind_rows(all_goalie_games) %>%
    mutate(Name = ifelse(SA_Goalie %in% goalie, SA_Goalie,NA))
  
  goalie_set <- all_goalie_starts %>%
    filter(SA_Goalie %in% goalie) %>%
    mutate(name_label = if_else(cum_SA == max(cum_SA), as.character(Name), NA_character_)) 

  # Overlay select Goalies on all Goalies limited to season  
  cum_xG_plot <- all_goalie_starts %>%
  ggplot(aes(x=cum_SA,y=cum_xG_Lift, group=SA_Goalie)) + 
    geom_line(color="grey25", alpha=0.4) +
    geom_line(data = goalie_set, size = 3, alpha = 0.8, aes(x=cum_SA,y=cum_xG_Lift, group=SA_Goalie, color=as.factor(Name))) +
    geom_line(data = goalie_set, size = 0.75, color="grey70", aes(x=cum_SA,y=cum_xG_Lift, group=SA_Goalie, alpha=as.factor(season))) +
    
    geom_hline(yintercept = 0, color="grey50") +
    theme_standard() + ggthemes::scale_color_gdocs() +
    labs(title=paste0("Goaltending Performance, Expected Goals Against - Actual Goals (Adjusted for Rebounds)\nAll Situations - ",glue::collapse(seasons, sep = ", ")),
         x="Cumulative Non-Rebound Shots Against", y="Expected Goals Against - Actual Goals", alpha="Season",
         color="Goalie") +
    annotate("text", x = 10, y = (max(all_goalie_games$cum_xG_Lift) * 0.8), hjust=0, label = "@CrowdScoutSprts\n(github.com/C92Anderson/xG-Model)") +
      ggrepel::geom_label_repel(data = goalie_set, aes(label = name_label, color=as.factor(Name)),
                  nudge_x = 1,
                  na.rm = TRUE) +
    theme(legend.position = "top") +
    guides(color = FALSE)
  
ggsave(filename=paste0("/Users/colander1/Downloads/cum_xG_plot",glue::collapse(seasons, sep = ""),".png"), plot=cum_xG_plot,  width=16, height=12)

return(cum_xG_plot)

}

QREAM_bygame_fun(c("JIMMY HOWARD","SERGEI BOBROVSKY","BRADEN HOLTBY","PEKKA RINNE","MARTIN JONES","CORY SCHNEIDER","FREDERIK ANDERSEN","CAREY PRICE","COREY CRAWFORD","JONATHAN QUICK","MATT MURRAY","MIKE SMITH","CAM TALBOT","HENRIK LUNDQVIST","ANDREI VASILEVSKIY","CRAIG ANDERSON","JAKE ALLEN","DEVAN DUBNYK"),c("20172018"))


#QREAM_bygame_fun(c("MICHAEL LEIGHTON","PETER BUDAJ","LOUIS DOMINGUE","ANTTI NIEMI","AL MONTOYA","CHARLIE LINDGREN"),c("20102011","20112012",                                        "20122013","20132014","20142015","20152016","20162017","20172018"))

#QREAM_bygame_fun(c("STEVE MASON","MIKE SMITH","ANTTI RAANTA","ONDREJ PAVELEC","BRIAN ELLIOTT"),c("20172018"))
#QREAM_bygame_fun(c("ANTON KHUDOBIN","TUUKKA RASK"),c("20172018"))


```
```{r}

QREAM_bycareer <- function(goalie, seasons=c("20072008","20082009","20092010","20102011","20112012",
                                        "20122013","20132014","20142015","20152016","20162017","20172018"), shot_cut=100) {
  
  library(dplyr)
  
  # Select Goalies, Order by season, game, shot
  all_goalie_games <- goalie_data_prep %>%
    filter(season %in% seasons) %>%
    group_by(SA_Goalie, season,  season2, Game_Id) %>%
    summarise(xG = sum(sum(xG_FirstShot) + ((sum(xR) * 0.26))),
              #xG = sum(xG),
              GA = sum(Goal),
              SA = sum(ifelse(is_Rebound == 0, 1, 0))) %>%
    group_by(SA_Goalie) %>%
    mutate(cum_xG = cumsum(xG),
           cum_GA = cumsum(GA),
           cum_SA = cumsum(SA),
           cum_xG_Lift = cum_xG - cum_GA)
  
  all_goalie_starts <- all_goalie_games %>% group_by(SA_Goalie) %>% top_n(1, -cum_SA) %>%
    mutate(cum_xG = 0,
           cum_GA = 0,
           cum_SA = 0,
           cum_xG_Lift = 0) %>%
    bind_rows(all_goalie_games) %>%
    mutate(Name = ifelse(SA_Goalie %in% goalie, SA_Goalie,NA))
  
  goalie_set <- all_goalie_starts %>%
    filter(SA_Goalie %in% goalie) %>%
    mutate(name_label = if_else(cum_SA == max(cum_SA), as.character(Name), NA_character_)) 

  # Overlay select Goalies on all Goalies limited to season  
  cum_xG_plot <- all_goalie_starts %>%
  ggplot(aes(x=cum_SA,y=cum_xG_Lift, group=SA_Goalie)) + 
    geom_line(color="grey25", alpha=0.4) +
    geom_line(data = goalie_set, size = 3, alpha = 0.8, aes(x=cum_SA,y=cum_xG_Lift, group=SA_Goalie, color=as.factor(season))) +
    geom_hline(yintercept = 0, color="grey50") +
    theme_standard() + ggthemes::scale_color_gdocs() +
    labs(title=paste0(goalie," Performance, Expected Goals Against - Actual Goals (Adjusted for Rebounds)\nAll Situations"),
         x="Cumulative Non-Rebound Shots Against", y="Expected Goals Against - Actual Goals", color="Season",
         color="Goalie") +
    annotate("text", x = 10, y = (max(all_goalie_games$cum_xG_Lift) * 0.8), hjust=0, label = "@CrowdScoutSprts\n(github.com/C92Anderson/xG-Model)") +
    geom_label(data = goalie_set, aes(label = name_label), color="grey50",
                  nudge_x = -5,
                  nudge_y = -4,
                  na.rm = TRUE) +
    theme(legend.position = "top")
  
ggsave(filename=paste0("/Users/colander1/Downloads/career_xG_plot",glue::collapse(seasons, sep = ""),".png"), plot=cum_xG_plot,  width=16, height=12)

return(cum_xG_plot)

}

QREAM_bycareer("BRIAN ELLIOTT")
```

## Team Story

```{r}

team_story <- function(team, year) {
  
  team_story <- scored_data %>%
    filter((Home_Team == team | Away_Team == team) & season == year) %>%
    filter(!(Season_Type == "RS" & Period == 5)) %>%
    filter(EmptyNet_SA == 0) %>%
    select(season, Game_Id, Home_Team, Away_Team, xG_team, Game_State, Goal, Ev_Team) %>%
    mutate(Game_Id = as.character(Game_Id),
           Strength = ifelse(Game_State %in% c("6v6","5v5","4v4","3v3"),"Even Strength xGF - xGA","Special Teams xGF - xGA"),
           Opposition = ifelse(Home_Team != team, as.character(Home_Team), as.character(Away_Team)),
           Home = ifelse(team == Home_Team, 1, 0),
           xGF = ifelse(Ev_Team == team,xG_team,0),
           xGA = ifelse(Ev_Team != team,xG_team,0),
           GF = ifelse(Ev_Team == team,Goal,0),
           GA = ifelse(Ev_Team != team,Goal,0)) %>%
    group_by(season, Game_Id, Opposition, Home, Strength) %>%
    summarise(xGF = sum(xGF),
              xGA = sum(xGA),
              GF = sum(GF),
              GA = sum(GA),
              xGD = xGF - xGA,
              GD = GF - GA)
  
  if(dim(team_story)[1] > 0) {
    
    team_rates <- team_story %>%
      dcast(season + Game_Id + Opposition + Home ~ Strength, value.var="xGD")
    
    team_bygame <- team_story %>%
      group_by(season, Game_Id, Opposition, Home) %>%
      summarise(xGF = sum(xGF),
                xGA = sum(xGA),
                GF = sum(GF),
                GA = sum(GA),
                GD = sum(GD)) %>%
      left_join(team_rates, by=c("season","Game_Id", "Opposition", "Home")) %>%
      mutate(`Shooting Lift (GF - xGF)` = GF - xGF,
             `Goaltending Lift (xGA - GA)` = xGA - GA,
             `Special Teams xGF - xGA`= ifelse(is.na(`Special Teams xGF - xGA`), 0, `Special Teams xGF - xGA`),
             Final = GF - GA) %>%
      as.data.frame()
    
    team_bygame$GameNum <- 1:nrow(team_bygame)     
    team_bygame$Team <- team
    
    game_chart <- team_bygame %>%
      melt(id.vars=c("season","GameNum","Final","Opposition"),
           measure.vars=c("Even Strength xGF - xGA","Goaltending Lift (xGA - GA)",
                          "Shooting Lift (GF - xGF)","Special Teams xGF - xGA")) %>%
      ggplot(aes(x=GameNum, y=value, fill=variable)) +
      #     annotate("text", x = 1, y = max(team_bygame$Final) + 0.5, hjust=0, size = 3, label = "@CrowdScoutSprts\nxG Model built using nhlscrapr\ngithub.com/C92Anderson/xG-Model") +
      #ylim(c(min(min(team_bygame$Final)-5), NA)) +
      geom_bar(stat="identity", colour="white") + 
      geom_text(aes(x=GameNum, y=Final, label=Opposition), angle = 90) +
      scale_y_continuous(breaks = seq( min(team_bygame$Final),max(team_bygame$Final), by=1)) +
      #scale_fill_gradient2(low="white",mid="light grey",high="Red") +
      theme_standard() + ggthemes::scale_fill_gdocs() +
      theme(panel.background = element_blank(),
            legend.position = "right",
            axis.title.x=element_blank(),
            axis.text.x=element_blank(),
            axis.ticks.x=element_blank()) +
     annotate("text", x = 1, y = -4, hjust=0, size = 3.5, label = "Opposition team label\nindicates game goal differential.") +
     labs(title=paste0(team," ",year," xG Components by Game - ", Sys.Date(), " YTD\nxG Adjusted for Multiplicativity\n@CrowdScoutSprts (github.com/C92Anderson/xG-Model)"),
           x="Game Number", y=paste0("xG Lift to ", team), fill="Team Component") 
    
    cum_chart <- team_bygame %>%
      group_by(season) %>%
      mutate(`Shooting Lift (GF - xGF)` = cumsum(`Shooting Lift (GF - xGF)`),
             `Goaltending Lift (xGA - GA)` = cumsum(`Goaltending Lift (xGA - GA)`),
             `Even Strength xGF - xGA` = cumsum(`Even Strength xGF - xGA`),
             `Special Teams xGF - xGA` = cumsum(`Special Teams xGF - xGA`),
             `Goal Differential` = cumsum(Final)) %>%
      as.data.frame() %>%
      melt(id.vars=c("season","GameNum","Goal Differential"),
           measure.vars=c("Even Strength xGF - xGA","Goaltending Lift (xGA - GA)",
                          "Shooting Lift (GF - xGF)","Special Teams xGF - xGA")) %>%
      ggplot() +
      theme_standard() + ggthemes::scale_color_gdocs() +
      theme(panel.background = element_blank(),
            legend.position = "right",
            axis.title.x=element_blank(),
            axis.text.x=element_blank(),
            axis.ticks.x=element_blank()) +
      annotate("segment",x=0,y=0,xend=max(team_bygame$GameNum),yend=0) +
      #annotate("text", x = 1, y = max(cumsum(team_bygame$Final)) + 1, hjust=0, size = 4, label = "@CrowdScoutSprts\nxG Model built using nhlscrapr\ngithub.com/C92Anderson/xG-Model") +
      annotate("text", x = 1, y = -4, hjust=0, size = 3.5, label = "Empty net and\nshootout goals removed") +
      #ylim(c(min(min(team_bygame$Final)-5), NA)) +
      geom_line(aes(x=GameNum-0.5, y=value, group=variable, color=variable), size=1.5) +
      geom_line(aes(x=GameNum-0.5, y=`Goal Differential`, group=1, color="Total GF - GA"), linetype = "dashed", size=2.5) +
      #scale_y_continuous(breaks = seq( min(team_bygame$value),max(team_bygame$value), by=1)) +
      labs(#title=paste0(team," ",season," Cumulative xG Components by Game - ", Sys.Date(), " YTD"),
        x="Game Number", y=paste0("Cumulative xG Lift to ", team), color="Cumulative\nTeam Component") 
    
      library(gridExtra)
      gA <- ggplotGrob(game_chart)
      gB <- ggplotGrob(cum_chart)
      maxWidth = grid::unit.pmax(gA$widths[2:5], gB$widths[2:5])
      gA$widths[2:5] <- as.list(maxWidth)
      gB$widths[2:5] <- as.list(maxWidth)

      p4 <- arrangeGrob(
        gA, gB, nrow = 2, heights = c(0.80, 0.80))
      
    ggsave(filename=paste0("/Users/colander1/Downloads/xG_story",team,".png"), plot=p4,  width=16, height=12)

    return(team_bygame)
  }
}

out <- team_story("VGK", "20172018")


```

## YTD Team Story Aggregated

```{r}

teams <- c("ATL","WSH","BOS","VAN","WPG","PHX","ANA","L.A","CAR","MTL","DET","OTT","TOR","COL","DAL","NYR","FLA","T.B","N.J","NSH","CHI","VGK",
           "MIN","CGY","PHI","EDM","S.J","STL","PHX","PIT","CBJ","NYI","BUF","ARI")
all_game_stories_1718 <- do.call(rbind,lapply(FUN=team_story,teams,"20172018"))


cum_game_stories_1718 <- all_game_stories_1718 %>%
      group_by(Team) %>%
      summarise(`Shooting Lift (GF - xGF)` = sum(`Shooting Lift (GF - xGF)`),
             `Goaltending Lift (xGA - GA)` = sum(`Goaltending Lift (xGA - GA)`),
             `Even Strength xGF - xGA` = sum(`Even Strength xGF - xGA`),
             `Special Teams xGF - xGA` = sum(`Special Teams xGF - xGA`),
             `Goal Differential` = sum(Final)) %>%
  melt(id.vars=c("Team","Goal Differential"),
       measure.vars=c("Even Strength xGF - xGA","Goaltending Lift (xGA - GA)",
                          "Shooting Lift (GF - xGF)","Special Teams xGF - xGA")) 
  
cum_game_stories_plot_1718 <- cum_game_stories_1718 %>%
  ggplot(aes(x=reorder(Team,`Goal Differential`), y=value, group=variable, fill=variable), alpha=0.75) +
  geom_bar(stat = "identity", position = "stack") +
  geom_hline(color="grey50", yintercept = 0, size = 3, alpha=0.6) +
  geom_label(aes(x=reorder(Team,`Goal Differential`),y=`Goal Differential`, label=ifelse(`Goal Differential` >= 0,paste0("+",`Goal Differential`),paste0(`Goal Differential`))), size=3, fill="grey85", alpha=0.75) +
  theme_standard() + ggthemes::scale_fill_gdocs() +
      theme(legend.position = "right",
            panel.grid.major.x = element_line( colour = "white", size = 2),
            panel.grid.major.y = element_line( colour = "white", size = 2)) +
  coord_flip() +
  labs(title=paste0("Team Goal Differential Explained by Cumulative xG Components, ", Sys.Date(), " YTD\nxG Adjusted for Multiplicativity, empty net and shootout goals removed\n@CrowdScoutSprts (github.com/C92Anderson/xG-Model)"),
           x="", y=paste0("xG Lift to Team"), fill="Team Component")


ggsave(filename=paste0("/Users/colander1/Downloads/cum_game_stories_plot_1718.png"), plot=cum_game_stories_plot_1718,  width=12, height=16)

team_strengths_plot_1718 <- cum_game_stories_1718 %>%
  group_by(variable) %>%
  mutate(Team_Rank = rank(-value)) %>%
  ggplot(aes(x=reorder(Team,value), y=value, fill=variable), alpha=0.75) +
  geom_bar(stat = "identity", position = "stack") +
  facet_grid(.~variable) +
  geom_hline(color="grey50", yintercept = 0, size = 3, alpha=0.6) +
  geom_label(aes(x=reorder(Team,value), y=-8, label=paste0("#",Team_Rank)),color="grey20", fill="grey75", alpha=0.7) +
  theme_standard() + ggthemes::scale_fill_gdocs() +
      theme(legend.position = "right",
            panel.grid.major.x = element_line( colour = "white", size = 2),
            panel.grid.major.y = element_line( colour = "white", size = 2)) +
  coord_flip() +
  labs(title=paste0("Team Goal Differential Explained by Cumulative xG Components, ", Sys.Date(), " YTD\nxG Adjusted for Multiplicativity, empty net and shootout goals removed\n@CrowdScoutSprts (github.com/C92Anderson/xG-Model)"),
           x="", y=paste0("xG Lift to Team"), fill="Team Component")

  
ggsave(filename=paste0("/Users/colander1/Downloads/team_strengths_plot_1718.png"), plot=team_strengths_plot_1718,  width=16, height=16)

```

## Shot Difficulty

```{r}

season_shot_difficulty_bar <- function(szn) {
  
# Calculate season-level xG Saved per 100 shots
goalie_season <- goalie_shot_level_prep %>%
      mutate(Strength = ifelse(Game_State %in% c("6v6","5v5","4v4","3v3"),"EV","ST")) %>%
      group_by(SA_Goalie, Strength, season) %>%
      summarise(xG_Lift_100Shots = (sum(xG) - sum(Goal)) / (n() / 100),
              NonRebound_Shots = sum(NonRebound_Shot),
              Shots = n(),
              GA = sum(Goal),
              SvPct = (Shots - sum(Goal)) / Shots, 
              xG_FirstShot = sum(xG_FirstShot),
              xG = sum(xG),
              xRebounds = sum(xR),
              RBA = sum(is_Rebound),
              xG_RB = sum(xR * rebound_goal_probability),
              
              xG_raw = sum(xG),
              xG_xR_Lift_100Shots = (sum(xG_FirstShot + xG_RB) -sum(Goal)) / (sum(NonRebound_Shot) / 100),

              posterior_xG_lift = bayes_lift_fun(xG, sum(Goal), Shots, 2000),

              posterior_xG_xR_lift = bayes_lift_fun(sum(xG_FirstShot + xG_RB), sum(Goal), NonRebound_Shots, 2000)) %>%
  filter(season == szn) %>%
  filter(nchar(as.character(SA_Goalie)) > 1) %>%
  group_by(SA_Goalie, season) %>%
  mutate(xSv = (NonRebound_Shots - (xG_RB + xG_FirstShot)) / NonRebound_Shots,
         Sv = (NonRebound_Shots - GA) / NonRebound_Shots,
         Total_NonRebound_Shots = sum(NonRebound_Shots))

xSv_range <- quantile(goalie_season$xSv, c(0.1,1))
ST_xSv <- goalie_season %>% filter(Strength == "ST") 
EV_xSv <- goalie_season %>% filter(Strength == "EV") 

# Plot shot difficulty
difficulty_plot <- goalie_season %>%
  filter((Total_NonRebound_Shots > (0.25 * max(goalie_season$Total_NonRebound_Shots)))) %>%
  arrange(desc(xSv)) %>%
  ggplot() +
  theme_standard() +
  facet_grid(.~Strength, scales = "free") +
  #geom_hline(yintercept = mean(goalie_season$xSv), color = "grey20") +
 
  geom_segment(aes(x = reorder(SA_Goalie,-xSv), 
                   y = xSv, xend = reorder(SA_Goalie,-xSv), yend = Sv, colour = (Sv - xSv)),size=2) +
  scale_color_gradient2(low="#DC3912",high="#109618", mid="#990099", labels = scales::percent) +
  geom_point(aes(x=reorder(SA_Goalie,-xSv), y=xSv, size = NonRebound_Shots), show.legend=TRUE, stat="identity", color="grey50") +
  geom_text(aes(x=reorder(SA_Goalie,-xSv), y=xSv, label="xSv%"), size=1.5, stat="identity", color="white") +

  geom_point(aes(x=reorder(SA_Goalie,-xSv), y=Sv, size = NonRebound_Shots), stat="identity", color="slateblue4") +
  geom_text(aes(x=reorder(SA_Goalie,-xSv), y=Sv, label="Sv%"),  size=1.5, stat="identity", color="white") +
  
  scale_y_continuous(labels = scales::percent) +
   coord_flip() +
  theme_standard() +
  theme(panel.background = element_blank(), 
        panel.grid.major.y = element_line(colour = "light grey", size = 0.1)) +
  labs(title=paste0("Goals Prevented Above Average, Adjusted for Rebounds, Sorted by xSv % ", szn,"\nGrey bubble: xSv% - Dark bubble: Actual Sv%\n@CrowdScoutSprts (github.com/C92Anderson/xG-Model)"),
       x="Goalie", y="(Expected) Sv %", color="Sv % Lift\nOver Expected", size = "Non-Rebound\nSeason Shots") +
  annotate("text", angle=90, label="Tougher Shots", y=xSv_range[1], x=35, size=7, color="grey50") +
  annotate("text", angle=-90, label="Easier Shots", y=xSv_range[2], x=15, size=7, color="grey50")

difficulty_plot

ggsave(filename=paste0("/Users/colander1/Downloads/difficulty_plot",szn,".png"), plot=difficulty_plot,  width=16, height=16)

}

season_shot_difficulty_bar("20172018")



season_shot_difficulty_scatter <- function(szn) {
  
# Calculate season-level xG Saved per 100 shots
goalie_team_season <- goalie_shot_level_prep %>%
      filter(season == szn) %>%
      filter(nchar(as.character(SA_Goalie)) > 1) %>%
      mutate(Strength = ifelse(Game_State %in% c("6v6","5v5","4v4","3v3"),"EV","ST")) %>%
      group_by(SA_Team, SA_Goalie, Strength, season) %>%
      summarise(xG_Lift_100Shots = (sum(xG) - sum(Goal)) / (n() / 100),
              NonRebound_Shots = sum(NonRebound_Shot),
              Shots = n(),
              GA = sum(Goal),
              SvPct = (Shots - sum(Goal)) / Shots, 
              xG_FirstShot = sum(xG_FirstShot),
              xG = sum(xG),
              xRebounds = sum(xR),
              RBA = sum(is_Rebound),
              xG_RB = sum(xR * rebound_goal_probability),
              
              xG_raw = sum(xG),
              xG_xR_Lift_100Shots = (sum(xG_FirstShot + xG_RB) -sum(Goal)) / (sum(NonRebound_Shot) / 100)) %>%
  group_by(SA_Team, SA_Goalie, season) %>%
  mutate(xSv = (NonRebound_Shots - (xG_RB + xG_FirstShot)) / NonRebound_Shots,
         Sv = (NonRebound_Shots - GA) / NonRebound_Shots,
          Goalie = paste0(sapply(strsplit(as.character(SA_Goalie), ' '), function(x) x[length(x)])),
         Total_Shots = sum(NonRebound_Shots),
         Performance = factor(ifelse((Sv-xSv) > 0.01,">1% (Very Good)",
                         ifelse((Sv-xSv) > 0,"0% - 1% (Good)",
                         ifelse((Sv-xSv) > -0.01,"-1% - 0% (Bad)",
                         "<-1% (Very Bad)"))),levels = c("<-1% (Very Bad)","-1% - 0% (Bad)","0% - 1% (Good)",">1% (Very Good)")))


xSv_range <- goalie_team_season %>% group_by(Strength) %>% do(data.frame(t(quantile(.$xSv, probs = c(0.1,0.5,0.9)))))
xSv_range$Strength <- as.factor(xSv_range$Strength)

# Plot shot difficulty
difficulty_plot <- goalie_team_season %>%
    group_by(SA_Team, season) %>%
    mutate(Team_Rank = weighted.mean(xSv, w=NonRebound_Shots)

                                ) %>%
    #filter((Total_Shots > (0.2 * max(Total_Shots))))  %>%

    ggplot(aes(x = reorder(interaction(SA_Team),-Team_Rank), y=xSv, size=NonRebound_Shots, color=Performance, shape=as.factor(Strength))) +
     geom_hline(data = plyr::ddply(goalie_team_season, "Strength", summarize, avg = mean(xSv)), aes(yintercept=avg), color="grey50", alpha=0.6) + ggrepel::geom_label_repel(aes(label=Goalie), size=3) + 
  #   geom_abline(slope = 1, intercept = 0, color = "grey50") +

     #geom_text(data = plyr::ddply(goalie_team_season, "Strength", summarize, min_Sv = mean(xSv)), aes(y=min_Sv, x=15, label="Tough Shots"), angle = 90) +
     #geom_hline(data = plyr::ddply(goalie_team_season, "Strength", summarize, avg = mean(xSv)), aes(yintercept=avg)) +
#    geom_hline(yintercept = mean(goalie_season$xSv), color = "grey50") +
    #facet_grid(.~Strength, scales = "free") +
    geom_point() +
    coord_flip() +
    scale_y_continuous(labels = scales::percent) +  
    #scale_color_gradient2(low="#DC3912",high="#109618", mid="#990099", labels = scales::percent) +
    theme(panel.grid.major.y = element_line( colour = "white", size = 2),
          panel.grid.minor.y = element_line( colour = "white", size = 2)) +
     theme_standard() + ggthemes::scale_color_gdocs() +
    labs(x="Team Ranked by Tougher Average Shots (Top) to Easier (Bottom)",y="Expected Sv %",fill="Shots Against", alpha="Measurement\n(Adjusting for Rebounds\nIncreases Predictivity)",
         size="Non-Rebound Shots Against",
         shape = "Strength",
         color = "Actual - Expected Sv % Lift",
         title=paste0("Shot Difficulty By Team and Strength, Adjusted for Rebounds, ",szn," YTD - ",Sys.Date(),"\n@crowdscoutsprts (github.com/C92Anderson/xG-Model)")) +
    annotate("text", angle = -90, x=length(unique(goalie_team_season$SA_Team))/2, y=0.95, color="grey50",size=5,label="Easier Shots") +
    annotate("text", angle = 90, x=length(unique(goalie_team_season$SA_Team))/1.25, y=0.88, color="grey50", size=5,label="Tougher Shots")


ggsave(filename=paste0("/Users/colander1/Downloads/xG_scatter_perShot_plot_",szn,".png"), plot=difficulty_plot,  width=16, height=20)

return(difficulty_plot)


}

season_shot_difficulty_scatter("20172018")
```

## Simulated Seasons

```{r}

simulated_seasons <- function(goalies, year=c("20102011","20112012","20122013","20132014","20142015","20152016","20162017","20172018"), sims) {
  
  season_shots <- scored_data %>%
    filter(SA_Goalie %in% goalies & season %in% year) %>%
    mutate(xG_total = ifelse(is_Rebound == 0, xG + (xR * 0.26), 0),
           NR_Shots = ifelse(is_Rebound == 0, 1, 0),
           Goalie_Season = paste0(sapply(strsplit(as.character(SA_Goalie), ' '), function(x) x[length(x)])," ",substr(season,7,8))) %>%
    select(xG_total, Goal, Game_Id, Goalie_Season, NR_Shots, season) 
  
  sim_QREAM <- matrix(nrow = sims, ncol=0)

  #For each goalie in data
  for(g in sort(unique(season_shots$Goalie_Season))) {
      
    print(g)
    goalie_shots <- season_shots %>% 
        filter(Goalie_Season == g) 
    
    print(dim(goalie_shots))
    
    sim_goalie_vec <- vector(length = sims)
    
    ## Loop through simulations
    for(s in 1:sims) { 
      
      set.seed(s)
      sim_outcome <- goalie_shots %>%
        rowwise() %>%
        # Simulated Goals
        mutate(sim_goals = rbinom(size=1, prob=xG_total, n=1)) %>%
        ungroup() %>%
        group_by() %>%
        summarise(sim = (sum(sim_goals) - sum(goalie_shots$Goal)) / sum(NR_Shots))
      
      sim_goalie_vec[s] <- sim_outcome[[1]]
      
    }
    
    ##Convert to sv%
    sim_QREAM <- cbind(sim_QREAM,sim_goalie_vec)
    
  }
  colnames(sim_QREAM) <- as.character(sort(unique(season_shots$Goalie_Season)))
  
  sim_QREAM2 <- sim_QREAM %>% melt()
  
  ## Plot histogram
  p1 <- sim_QREAM2 %>%
    ggplot() +
    geom_density(aes(x=value, fill=Var2, group=Var2, color=Var2), stat = "density", position = "identity", alpha=0.3) +
    theme_standard() + ggthemes::scale_fill_gdocs() +  ggthemes::scale_color_gdocs()  +
    scale_x_continuous(labels = scales::percent) +
    labs(title=paste0(paste(goalies,sep="", collapse=", ")," ",paste(year,sep="", collapse=", ")," Performance\nObserved Sv% - Simulated Expected Sv% (",sims, " Simulations)\n@CrowdScoutSprts (github.com/C92Anderson/xG-Model)"),
         x="Observed Sv% - Simulated Expected Sv%", y="Density", fill="Goalie Season", color="Goalie Season") +
    annotate("segment", x=0, xend=0, y=0, yend=0.1, color="grey") 
 
  ggsave(filename=paste0("/Users/colander1/Downloads/sim_seasons_",paste(goalies,sep="", collapse="_"),".png"), plot=p1,  width=16, height=12)
 
  return(list(p1))
  
}


simulated_seasons(goalies = c("MATT MURRAY"), year = c("20152016","20162017","20172018"), sims = 1000)


```

##Shot Distance by Team, Strength, Position

```{r}

team_list <- unique(scored_data$Home_Team)

team_shots <- function(team) {
  team_shots <- scored_data %>%
    filter(Home_Team == team | Away_Team == team) %>%
    mutate(Rink = ifelse(Home_Team == team,"Home_Rink","Away_Rink"),
           Home_Team = ifelse(Home_Team %in% c("ATL"),"WPG",as.character(Home_Team))) %>%
    dplyr::select(season, Rink, Event, Ev_Team, Home_Team,Player_Position2, Away_Team, Shooter_State, Goalie_State, Shot_Distance, Shot_Distance_Unadj, xG, xG_team) %>%
    mutate(Team = team)
}


shots_home_away <- plyr::rbind.fill(lapply(FUN=team_shots,team_list))

team_venue_shot_distance <- shots_home_away %>%
  filter(season == "20172018") %>%
  mutate(Strength = ifelse(Shooter_State > Goalie_State, "Powerplay",
                                   ifelse(Shooter_State == Goalie_State, "Even Strength","SH"))) %>% 
  filter(!Strength %in% c("SH"))

team_venue_shot_distance_sums <- team_venue_shot_distance %>%
  group_by(Team, Strength, Player_Position2) %>%
  summarise(Unadjusted = mean(Shot_Distance_Unadj, na.rm=T),
            `CDF Adjusted` = mean(Shot_Distance, na.rm=T),
            Adjustment = Unadjusted - `CDF Adjusted`) %>%
  melt(id.vars = c("Team","Strength","Adjustment","Player_Position2") , value.name = "Mean") %>%
#  group_by(Strength, variable) %>%
  filter(variable == "CDF Adjusted") %>%
  
  arrange(Strength, variable, -Mean) %>%
  mutate(Order = row_number())
 
### Position Splits
team_venue_shot_distance_plot <- team_venue_shot_distance %>%
  mutate(`CDF Adjusted` = Shot_Distance,
         Unadjusted = Shot_Distance_Unadj) %>%
  select(Team, Strength, `CDF Adjusted`, Unadjusted, Player_Position2) %>%
  melt(id.vars = c("Team","Strength","Player_Position2"), value.name = "value") %>%
  filter(variable == "CDF Adjusted") %>%
  left_join(team_venue_shot_distance_sums, by = c("Team","Strength","variable","Player_Position2")) %>%
  #filter(Strength %in% c("EV","PP")) %>%
  ggplot(aes(x=value,y=as.factor(Order),fill=Player_Position2),alpha=.25) +
  #ggjoy::geom_joy(alpha=.25) +
  ggridges::geom_density_ridges2(alpha=0.5) +
  #geom_label(aes(x=Mean, y=as.factor(Order), color=Strength, label=paste0(round(Mean,1),"ft"))) +
  xlim(0,100) +
  facet_wrap(Strength~Player_Position2, scales = "free") +
  # Add categories to axis
  scale_y_discrete(
    breaks = team_venue_shot_distance_sums$Order,
    labels = team_venue_shot_distance_sums$Team,
    expand = c(0,0)
  ) +
  scale_fill_gradient2(low="#990099",high="#DC3912", mid="grey75", midpoint = 0) +
  geom_text(data = team_venue_shot_distance_sums, aes(x=Mean, y=as.factor(Order), label=paste0(round(Mean,1),"ft")), 
            nudge_y = 0.5, stat = "identity", color="grey30") +
  theme_standard() + ggthemes::scale_fill_gdocs() + ggthemes::scale_color_gdocs() +
  labs(y="",x="Shot Distance From Net",
       fill="Shooter Position",
       title="Shot Distance For by Team, Strength, and Position, 2017-18") +
  theme(legend.position = "top")

 ggsave(filename=paste0("/Users/colander1/Downloads/team_venue_shot_distance_plot.png"), plot=team_venue_shot_distance_plot,  width=12, height=16)
 
 
### Splits by Season
team_venue_shot_distance_bySeason <- shots_home_away %>%
  filter(season %in% c("20152016","20162017","20172018")) %>%
  mutate(Strength = ifelse(Shooter_State > Goalie_State, "Powerplay",
                                   ifelse(Shooter_State == Goalie_State, "Even Strength","SH"))) %>% 
  filter(!Strength %in% c("SH"))

team_venue_shot_distance_sums <- team_venue_shot_distance_bySeason %>%
  group_by(season, Team, Strength, Player_Position2) %>%
  summarise(`CDF Adjusted` = mean(Shot_Distance, na.rm=T)) %>%
  melt(id.vars = c("season","Team","Strength","Player_Position2") , value.name = "Mean") %>%
#  group_by(Strength, variable) %>%
  filter(variable == "CDF Adjusted") %>%
  arrange(Strength, variable, -Mean) %>%
  mutate(Order = row_number())
 
### Position Splits
team_venue_shot_distance_plot <- team_venue_shot_distance %>%
  mutate(`CDF Adjusted` = Shot_Distance,
         Unadjusted = Shot_Distance_Unadj) %>%
  select(Team, Strength, `CDF Adjusted`, Unadjusted, Player_Position2) %>%
  melt(id.vars = c("Team","Strength","Player_Position2"), value.name = "value") %>%
  filter(variable == "CDF Adjusted") %>%
  left_join(team_venue_shot_distance_sums, by = c("Team","Strength","variable","Player_Position2")) %>%
  #filter(Strength %in% c("EV","PP")) %>%
  ggplot(aes(x=value,y=as.factor(Order),fill=Player_Position2),alpha=.25) +
  #ggjoy::geom_joy(alpha=.25) +
  ggridges::geom_density_ridges2(alpha=0.5) +
  #geom_label(aes(x=Mean, y=as.factor(Order), color=Strength, label=paste0(round(Mean,1),"ft"))) +
  xlim(0,100) +
  facet_wrap(Strength~Player_Position2, scales = "free") +
  # Add categories to axis
  scale_y_discrete(
    breaks = team_venue_shot_distance_sums$Order,
    labels = team_venue_shot_distance_sums$Team,
    expand = c(0,0)
  ) +
  scale_fill_gradient2(low="#990099",high="#DC3912", mid="grey75", midpoint = 0) +
  geom_text(data = team_venue_shot_distance_sums, aes(x=Mean, y=as.factor(Order), label=paste0(round(Mean,1),"ft")), 
            nudge_y = 0.5, stat = "identity", color="grey30") +
  theme_standard() + ggthemes::scale_fill_gdocs() + ggthemes::scale_color_gdocs() +
  labs(y="",x="Shot Distance From Net",
       fill="Shooter Position",
       title="Shot Distance For by Team, Strength, and Position, 2017-18") +
  theme(legend.position = "top")

 ggsave(filename=paste0("/Users/colander1/Downloads/team_venue_shot_distance_plot.png"), plot=team_venue_shot_distance_plot,  width=12, height=16)

```

## Team WOWY Shot Locations

```{r}

team_wowy_shot_locations <- function(szn, team, player1, player2) {
      
    ### Splits by Season
    team_wowy_distance <- scored_data %>%
      filter(season %in% szn) %>%
      filter(Ev_Team == team) %>%
      mutate(Team = Ev_Team,
             Strength = ifelse(Shooter_State > Goalie_State, "Powerplay",
                                       ifelse(Shooter_State == Goalie_State, "Even Strength","SH")),
             Team_Class = ifelse(player1 == awayPlayer1 | player1 == awayPlayer2 | player1 == awayPlayer3 | player1 == awayPlayer4 | player1 == awayPlayer5 | player1 == awayPlayer6 | player1 == homePlayer1 | player1 == homePlayer2 | player1 == homePlayer3 | player1 == homePlayer4 | player1 == homePlayer5 | player1 == homePlayer6, player1,
                          ifelse(player2 == awayPlayer1 | player2 == awayPlayer2 | player2 == awayPlayer3 | player2 == awayPlayer4 | player2 == awayPlayer5 | player2 == awayPlayer6 | player2 == homePlayer1 | player2 == homePlayer2 | player2 == homePlayer3 | player2 == homePlayer4 | player2 == homePlayer5 | player2 == homePlayer6, player2,                                 
                                 "OTHER" ))) %>% 
      filter(!Strength %in% c("SH"))
    
    team_wowy_distance_sums <- team_wowy_distance %>%
      group_by(season, Team, Team_Class, Strength, Player_Position2) %>%
      summarise(Mean_Distance = mean(Shot_Distance, na.rm=T),
                Sample = n()) %>%
      group_by(season, Team, Team_Class, Strength) %>%
      mutate(F_Share = max(ifelse(Player_Position2 == "F", Sample, 0)) / sum(Sample),
             Share = Sample / sum(Sample)) %>%
      filter(Sample > 12)
     
    ### Position Splits
    team_wowy_distance_plot <- team_wowy_distance %>%
      select(Team_Class, Team, Strength, Shot_Distance, Player_Position2) %>%
      inner_join(team_wowy_distance_sums, by = c("Team_Class","Team","Strength","Player_Position2")) %>%
      ggplot(aes(x=Shot_Distance,y=interaction(season,Team_Class,sep = "\n",lex.order = TRUE), fill=F_Share,alpha=Sample)) +
      #ggjoy::geom_joy(alpha=.25) +
      ggridges::geom_density_ridges2() +
      #geom_label(aes(x=Mean, y=as.factor(Order), color=Strength, label=paste0(round(Mean,1),"ft"))) +
      xlim(0,100) +
      facet_wrap(Strength~Player_Position2, scales = "free") +
      scale_fill_gradient2(low="#990099",high="#DC3912", mid="grey75", midpoint = median(team_wowy_distance_sums$F_Share), labels = scales::percent) +
      geom_label(data = team_wowy_distance_sums, aes(x=85, y=interaction(season,Team_Class,sep = "\n", lex.order = TRUE), label=paste0(round(Mean_Distance),"ft\n",round(Share,2)*100,"%")), 
              color="grey40", nudge_y = 0.5, stat = "identity") +
      geom_point(data = team_wowy_distance_sums, aes(x=Mean_Distance, y=interaction(season,Team_Class,sep = "\n", lex.order = TRUE)), size=4, alpha=0.8, color="grey30") +
      theme_standard() + ggthemes::scale_color_gdocs() +
      scale_alpha_continuous(range = c(0.5, 0.95)) +
      labs(y="",x="Shot Distance From Net",
           fill="% Shots From Forwards", alpha="Shots",
           title=paste0(team, " Shot Attempt Distance Distributions\nStrength and Shooter Position - ",glue::collapse(szn, sep = ", "),"\nWith And Without ",player1,", ",player2)) +
      theme(legend.position = "top")
    
     ggsave(filename=paste0("/Users/colander1/Downloads/",team,"_wowy_distance_plot.png"), plot=team_wowy_distance_plot,  width=12, height=16)

}

team_wowy_shot_locations(c("20152016","20162017","20172018"),"EDM","CONNOR MCDAVID","RYAN NUGENT-HOPKINS")

```
## Shooter xGF vs GF

```{r}

xG_v_GF_pershot <- function(player,   seasons=c("20072008","20082009","20092010","20102011","20112012",
                                                "20122013","20132014","20142015","20152016","20162017","20172018")) {
  
  player_stats <- scored_data %>%
    filter(Game_State %in% c("6v6","5v5")) %>%
    filter(p1_name == player & season %in% seasons) %>%
    mutate(Player = p1_name,
           season = as.character(season),
           SF = 1,
           GF = Goal) %>%
    group_by(Player, season) %>%
    summarise(#SF = sum(SF),
              `Actual Goals` = sum(GF),
              `Expected Goals`  = sum(xG),
              GF = sum(GF),
              xG = sum(xG),
              Mean_Shot_Distance = mean(Shot_Distance),
              Mean_Shot_Angle = mean(Shot_Angle),
              `ixG per Game` = sum(xG) / uniqueN(Game_Id),
              `Goals per Game` = sum(GF) / uniqueN(Game_Id),
              `iFF per GP` = sum(SF) / uniqueN(Game_Id),
              `xG per Shot` = sum(xG) / sum(SF),
              `GF per Shot` = sum(GF) / sum(SF))

  
  per_basis_data <- player_stats %>%
  dplyr::select(Player, season, ends_with("per Game"),
                                               ends_with("per Shot")) %>%  
    reshape2::melt(id.vars = c("Player", "season")) %>%
    mutate(Metric = ifelse(variable %in% c("ixG per Game", "Goals per Game"),"Per Game",
                    ifelse(variable %in% c("Total Goals For", "Total xGoals For"),"Total",
                    ifelse(variable %in% c("xG per Shot", "GF per Shot"),"Per Shot",""
                           ))),
           Measure = ifelse(variable %in% c("ixG per Game", "Total xGoals For", "xG per Shot"),"Expected Goals","Actual Goals")) 
    
per_shot <- per_basis_data %>%
    filter(Metric == "Per Shot") %>%
    ggplot() +
    geom_point(aes(x=season, y=value, group=Measure,color=Measure)) +
    geom_line(aes(x=season, y=value, group=Measure,color=Measure)) +
    labs(color="") +
    theme_standard() + ggthemes::scale_color_gdocs() +
    facet_grid(.~Metric, scale="free_y") +
    scale_y_continuous(labels = scales::percent, limits = c(0, NA)) +
    labs(title=paste0(player, " 5v5 Goal Production vs Expected by Season\n@CrowdScoutSprts (github.com/C92Anderson/xG-Model)")) +
    labs(y="Individual xG and GF per Shot Taken", x="", color="") +
    #annotate("text", x = 1, y = .025, hjust=0, label = "@CrowdScoutSprts\nxG Model built using nhlscrapr\ngithub.com/C92Anderson/xG-Model") +
    theme(panel.background = element_blank(),
          axis.title.x=element_blank(),
          panel.grid.major.y = element_line( colour = "white", size = 2), 
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank())
  
    
per_game <- per_basis_data %>%
    filter(Metric == "Per Game") %>%
    ggplot() +
    geom_point(aes(x=season, y=value, group=Measure,color=Measure)) +
    geom_line(aes(x=season, y=value, group=Measure,color=Measure)) +
    labs(color="") +
    theme_standard() + ggthemes::scale_color_gdocs() +
    facet_grid(.~Metric, scale="free_y") +
    scale_y_continuous(limits = c(0, NA)) +
    #labs(title=paste0(player, " Goal Production vs Expected by Season\n@CrowdScoutSprts (github.com/C92Anderson/xG-Model)")) +
    labs(y="Individual xG and GF per Game Played", x="", color="") +
    #annotate("text", x = 1, y = .025, hjust=0, label = "@CrowdScoutSprts\nxG Model built using nhlscrapr\ngithub.com/C92Anderson/xG-Model") +
    theme(panel.background = element_blank(),
          axis.title.x=element_blank(),
          panel.grid.major.y = element_line( colour = "white", size = 2), 
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank())
    

  absolute <- player_stats %>%
    dplyr::select(Player, season, `Actual Goals`, `Expected Goals`, `iFF per GP`) %>%
    as.data.frame() %>%
    reshape2::melt(id.vars = c("Player", "season","iFF per GP")) %>%
    mutate(Metric = "Absolute Totals") %>%
    ggplot() +
    facet_grid(.~Metric, scale="free_y") +
    ylim(c(0,NA)) +
    geom_bar(aes(x=season, y=value, group=variable,fill=variable), position="dodge", stat="identity") +
    geom_text(data=player_stats,aes(x=season, y=min(player_stats$xG) / 2,
                                    label=paste0(round(`iFF per GP`,1)," iFF/GP\n",round(Mean_Shot_Distance,1),"ft\n",round(Mean_Shot_Angle,1),""))) + 
     theme_standard() + ggthemes::scale_fill_gdocs() +
   labs(color="") +
    #labs(title=paste0(player, " xG and GF by Season")) +
    labs(x="Season", y="Individual xG and GF", fill="") +
    theme(#legend.position = "top",
          panel.grid.major.y = element_line( colour = "white", size = 2))
  
  # Plot two graphs together
  library(gridExtra)
  gA <- ggplotGrob(per_shot)
  gC <- ggplotGrob(per_game)
  gB <- ggplotGrob(absolute)
  maxWidth = grid::unit.pmax(gA$widths[2:5], gC$widths[2:5], gB$widths[2:5])
  gA$widths[2:5] <- as.list(maxWidth)
  gB$widths[2:5] <- as.list(maxWidth)
  gC$widths[2:5] <- as.list(maxWidth)
  
  p4 <- arrangeGrob(
    gA, gC, gB, nrow = 3, heights = c(0.80, 0.80, 0.80))
    #return(out)

 ggsave(filename=paste0("/Users/colander1/Downloads/",player,"_shooting_bySeason2.png"), plot=p4,  width=12, height=16)
 

  
}

xG_v_GF_pershot("ERIK KARLSSON")
#xG_v_GF_pershot("SEAN MONAHAN")

```